---
title: "Chimps and Children compared"
author: "Eva Reindl"
date: "27 8 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
BothSpecies <-read.csv("ChimpsAndChildren.csv",header=TRUE, sep = ";")
library(ggplot2)
library(cowplot)
names(BothSpecies)[1] <- "ID"
str(BothSpecies)
```

# WM Updating
```{r}
sum(is.na(BothSpecies$WMUpdating))
```
1 missing value, so N = 237

Boxplot:
```{r}
p1<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=WMUpdating, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Updating")+
  geom_hline(yintercept=0.57965, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p1
```

# WM Grid
```{r}
sum(is.na(BothSpecies$WMGrid))
```
58 missing values, so N = 180

Boxplot:
```{r}
p2<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=WMGrid, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean distance")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Grid")+
  geom_hline(yintercept=0.5376574, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p2
```

# WM Boxes
```{r}
sum(is.na(BothSpecies$WMBoxes))
```
36 missing values, so N = 202

Boxplot:
```{r}
p3<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=WMBoxes, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Boxes")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p3
```

# Inhibition Boxes
```{r}
sum(is.na(BothSpecies$GlassCeiling))
```
59 missing values, so N = 179

Boxplot:
```{r}
p4<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=GlassCeiling, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Boxes")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p4
```

# Inhibition Cylinder
```{r}
sum(is.na(BothSpecies$Cylinder))
```
43 missing values, so N = 195

Boxplot:
```{r}
p5<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=Cylinder, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Cylinder")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p5
```

# Inhibition Grid
```{r}
sum(is.na(BothSpecies$InhibGrid))
```
43 missing values, so N = 211

Boxplot:
```{r}
p6<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=InhibGrid, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Grid")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p6
```

# Shifting Tray
```{r}
sum(is.na(BothSpecies$Tray))
```
38 missing values, so N = 200

Boxplot:
```{r}
p7<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=Tray, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Shifting Tray")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p7
```

# Shifting Shelf
```{r}
sum(is.na(BothSpecies$Shelf))
```
36 missing values, so N = 202

Boxplot:
```{r}
p8<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=Shelf, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop of switches")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Shifting Shelf")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p8
```

# Shifting Boxes
```{r}
sum(is.na(BothSpecies$CD_all))
```
53 missing values, so N = 185

Boxplot:
```{r}
p9<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=CD_all, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Shifting Boxes")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p9
```

# Reversal
```{r}
sum(is.na(BothSpecies$Reversal))
```
83 missing values, so N = 155

Boxplot:
```{r}
p10<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=Reversal, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Reversal")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())  +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p10
```

# EDS
```{r}
sum(is.na(BothSpecies$EDS))
```
160 missing values, so N = 78

Boxplot:
```{r}
p11<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=EDS, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("EDS")+
 geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p11
```


# SD
```{r}
sum(is.na(BothSpecies$SD))
```
43 missing values, so N = 195

Boxplot:
```{r}
p12<-  ggplot(
  data=BothSpecies, aes(x=rep(1, 238), y=SD, fill = Species))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean prop correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("SD")+
geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5)+
  theme(legend.position = "none")
p12
```

```{r fig.height=15, fig.width=10}
plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, rel_widths = c(1, 1,1), rel_heights = c(4,4,4,4), ncol = 3, nrow = 4)
```