---
title: "Scrambled_Boxes"
author: "Eva Reindl"
date: "18 9 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Scrambled <-read.csv("Scrambled.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
#recode variables
names(Scrambled)[1] <- "ID"

str(Scrambled)
```

# How many children are in the dataset? 
```{r}
Scrambled.FirstTrialFirstRound<- subset(Scrambled, Trial =="1" & RoundNr =="1")
```
There are 198 children in the dataset.

# Dropouts
```{r}
Scrambled.dropouts<- subset(Scrambled, StoppedEarly == "yes")
```
One child (D 172) stopped the game after 6 rounds in the first trial. This child will be excluded from further analyses.

# Valid data
```{r}
Scrambled.valid<- subset(Scrambled, StoppedEarly == "no")
```
**197 children have valid data** on the Scrambled box task.

# Sample description
## Gender distribution
```{r}
Scrambled.valid.FirstTrialFirstRound <- subset(Scrambled.valid, Trial =="1" & RoundNr =="1")
table(Scrambled.valid.FirstTrialFirstRound$Gender)
```
There are 109 females and 88 males.

## Age
### Age at beginning of testing
```{r}
mean(Scrambled.valid.FirstTrialFirstRound$Age_months)
sd(Scrambled.valid.FirstTrialFirstRound$Age_months)
min(Scrambled.valid.FirstTrialFirstRound$Age_months)
max(Scrambled.valid.FirstTrialFirstRound$Age_months)
hist(Scrambled.valid.FirstTrialFirstRound$Age_months)

table(Scrambled.valid.FirstTrialFirstRound$Age_group)
```
Children who contributed to this task were, at the beginning of testing, on average 48.60 months old (SD = 6.87, range 35-70). There were 1 2-year-old, 88 3-year-olds, 98 4-year-olds, and 10 5-year-olds.

## Age in the middle of testing
```{r}
mean(Scrambled.valid.FirstTrialFirstRound$Midtesting_age_months)
sd(Scrambled.valid.FirstTrialFirstRound$Midtesting_age_months)
min(Scrambled.valid.FirstTrialFirstRound$Midtesting_age_months)
max(Scrambled.valid.FirstTrialFirstRound$Midtesting_age_months)
hist(Scrambled.valid.FirstTrialFirstRound$Midtesting_age_months)

table(Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group)
```
Children in this task were on average **49.63 months old (SD = 6.87, range 36-72)** when they were in the middle of the test battery. There were 

- 86 3-year-olds
- 97 4-year-olds
- 13 5-year-olds
- 1 6-year-old

## Age mediansplit
```{r}
table(Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample)
```
There are **97 young** and **100 old** children.

# Testing location
```{r}
table(Scrambled.valid.FirstTrialFirstRound$TestingLocation)
```
120 children were from Fife, 77 children were from Edinburgh.

# Trial 1
## Total number of rounds administered
```{r}
mean(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds)
sd(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds)
min(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds)
max(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds)

tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.FirstTrialFirstRound$TotalNr_Rounds, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 1, the total number of administered trials was 9.15 (SD = 1.22, range 8-11).

- 3y: 9.24 (SD = 1.21, range 8-11)
- 4y: 9.05 (SD = 1.25, range 8-11)
- 3y: 9.38 (SD = 1.12, range 8-11)
- 3y: 8 

- Edinburgh: 9.09 (SD = 1.25, range 8-11)
- Fife: 9.19 (SD = 1.21, range 8-11)

- young: 9.23 (SD = 1.19, range 8-11)
- old: 9.08 (SD = 1.25, 8-11)

## Emptied all boxes
```{r}
table(Scrambled.valid.FirstTrialFirstRound$emptied_all_boxes)

table(Scrambled.valid.FirstTrialFirstRound$emptied_all_boxes, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group)

table(Scrambled.valid.FirstTrialFirstRound$emptied_all_boxes, Scrambled.valid.FirstTrialFirstRound$TestingLocation)

table(Scrambled.valid.FirstTrialFirstRound$emptied_all_boxes, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample)
```
161 children (82%) emptied all boxes, 36 did not.

- 3y: 71 yes (93%), 15 no
- 4y: 79 yes (81%), 18 no
- 5y: 10 yes (77%), 3 no
- 6y: 1y 

- Edinburgh: 64 yes (83%), 13 no
- Fife: 97 yes (80%), 23 no

- young: 81 yes (83%), 16 no
- old: 80 yes (80%), 20 no

## Number of boxes emptied
```{r}
mean(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied)
sd(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied)
min(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied)
max(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied)

tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.FirstTrialFirstRound$NrBoxesEmptied, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 1, the total number of emptied boxes was 7.79 (SD = 0.48, range 5-8).

- 3y: 7.78 (SD = 0.54, range 5-8)
- 4y: 7.80 (SD = 0.42, range 6-8)
- 5y: 7.77 (SD = 0.44, range 7-8)
- 6y: 8 

- Edinburgh: 7.82 (SD = 0.42, range 6-8)
- Fife: 7.77 (SD = 0.51, range 5-8)

- young: 7.79 (SD = 0.52, range 5-8)
- old: 7.79 (SD = 0.43, range 6-8)

## Effiency
```{r}
mean(Scrambled.valid.FirstTrialFirstRound$Efficiency)
sd(Scrambled.valid.FirstTrialFirstRound$Efficiency)
min(Scrambled.valid.FirstTrialFirstRound$Efficiency)
max(Scrambled.valid.FirstTrialFirstRound$Efficiency)

shapiro.test(Scrambled.valid.FirstTrialFirstRound$Efficiency)
hist(Scrambled.valid.FirstTrialFirstRound$Efficiency,
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.FirstTrialFirstRound$Efficiency, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 1, mean efficiency was 0.87 (SD = 0.14, range 0.45-1).

- 3y: 0.86 (SD = 0.14, range 0.45-1)
- 4y: 0.88 (SD = 0.14, range 0.54-1)
- 5y: 0.84 (SD = 0.13, range 0.64-1)
- 6y: 1

- Edinburgh: 0.88 (SD = 0.14, range 0.54-1)
- Fife: 0.86 (SD = 0.14, range 0.45-1)

- young: 0.86 (SD = 0.14, range 0.45-1)
- old: 0.88 (SD = 0.15, range 0.54-1)

## For those children wo did make an error, how many correct trials did they have before the first error occurred?
```{r}
Scrambled.valid.FirstTrialFirstRound.mademistake <- subset(Scrambled.valid.FirstTrialFirstRound, NoSearches_before_FirstError != "no error")

mean(Scrambled.valid.FirstTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
sd(Scrambled.valid.FirstTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
min(Scrambled.valid.FirstTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
max(Scrambled.valid.FirstTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
```
110 children made an error. Those children had an average of 5.35 (SD = 1.85, range 1-7) rounds correct before making the first error.

## Efficiency when disregarding the first trial 
So that efficiency could also be 0
```{r}
mean(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch)
sd(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch)
min(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch)
max(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch)

shapiro.test(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch)
hist(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch,
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.FirstTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.FirstTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 1, mean efficiency was 0.86 (SD = 0.16, range 0.40-1).

- 3y: 0.84 (SD = 0.16, range 0.4-1)
- 4y: 0.87 (SD = 0.16, range 0.5-1)
- 5y: 0.82 (SD = 0.15, range 0.6-1)
- 6y: 1

- Edinburgh: 0.87 (SD = 0.16, range 0.5-1)
- Fife: 0.85 (SD = 0.16, range 0.4-1)

- young: 0.85 (SD = 0.15, range 0.4-1)
- old: 0.86 (SD = 0.16, range 0.5-1)



## Can Success be predicted by age?
```{r}
Scrambled.valid.T1 <- subset(Scrambled.valid, Trial == "1" & RoundNr !="1")
#we z-transform age 
Scrambled.valid.T1$z.age.midtesting=as.vector(scale(Scrambled.valid.T1$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(Scrambled.valid.T1$z.age.midtesting)#check whether it has worked
sd(Scrambled.valid.T1$z.age.midtesting)

Scrambled.valid.T1$z.round=as.vector(scale(Scrambled.valid.T1$RoundNr))
mean(Scrambled.valid.T1$z.round)#check whether it has worked
sd(Scrambled.valid.T1$z.round)

library(lme4)
res<-glmer(Correct ~ z.age.midtesting + z.round + z.age.midtesting:z.round + (1|ID), data=Scrambled.valid.T1, family = binomial)#singular fit

null<-glmer(Correct ~ 1 + (1|ID), data=Scrambled.valid.T1, family = binomial)#singular fit

anova(null, res, test="Chisq")
```
Together, trial number, age, and the interaction explain the data better than a null model, X2(3) = 307.37, p < .001.

```{r}
res.nointer<-glmer(Correct ~ z.age.midtesting + z.round + (1|ID), data=Scrambled.valid.T1, family = binomial)

anova(res.nointer, res, test="Chisq")
```
The interaction term has a significant effect, X2(1) = 23.125, p < .001.

```{r}
three <- subset(Scrambled.valid.T1, Midtesting_age_group == "3")
#we z-transform age 
three$z.age.midtesting=as.vector(scale(three$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(three$z.age.midtesting)#check whether it has worked
sd(three$z.age.midtesting)

three$z.round=as.vector(scale(three$RoundNr))
mean(three$z.round)#check whether it has worked
sd(three$z.round)

library(lme4)
res<-glmer(Correct ~ z.round + (1|ID), data=three, family = binomial)#singular fit

null<-glmer(Correct ~ 1 + (1|ID), data=three, family = binomial)#singular fit

anova(null, res, test="Chisq")
```

```{r}
#plotting trial no with CIs
source("boot_glmm.r")
#requires centering of all predictors apart the ones one is interested in. We are interested in both.
boot.res=boot.glmm.pred(model.res=res, excl.warnings=T,
nboots=1000, para=F, resol=10, use="z.round")
boot.res$ci.estimates
boot.res$ci.predicted

par(mar=c(3, 3, 0.2, 0.2), mgp=c(1.7, 0.3, 0), las=1, tcl=-0.15)
plot(x=three$RoundNr, y=three$Correct, pch=19, las=2, ylim=c(0, 1),
xlab="Trial number", ylab="Probability of success", main = "3-year-olds")
plot.xvals=seq(from=min(three$RoundNr), to=max(three$RoundNr),
length.out=10)
lines(x=plot.xvals, y=boot.res$ci.predicted$fitted,
lty=2)
lines(x=plot.xvals, y=boot.res$ci.predicted$lower.cl,
lty=3)
lines(x=plot.xvals, y=boot.res$ci.predicted$upper.cl,
lty=3)
```


```{r}
four <- subset(Scrambled.valid.T1, Midtesting_age_group == "4")
#we z-transform age 
four$z.age.midtesting=as.vector(scale(four$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(four$z.age.midtesting)#check whether it has worked
sd(four$z.age.midtesting)

four$z.round=as.vector(scale(four$RoundNr))
mean(four$z.round)#check whether it has worked
sd(four$z.round)

library(lme4)
res1<-glmer(Correct ~ z.round + (1|ID), data=four, family = binomial)#singular fit

null<-glmer(Correct ~ 1 + (1|ID), data=four, family = binomial)

anova(null, res1, test="Chisq")
```

```{r}
boot.res=boot.glmm.pred(model.res=res1, excl.warnings=T,
nboots=1000, para=F, resol=10, use="z.round")
boot.res$ci.estimates
boot.res$ci.predicted

par(mar=c(3, 3, 0.2, 0.2), mgp=c(1.7, 0.3, 0), las=1, tcl=-0.15)
plot(x=four$RoundNr, y=four$Correct, pch=19, las=2, ylim=c(0, 1),
xlab="Trial number", ylab="Probability of success", main = "4-year-olds")
plot.xvals=seq(from=min(four$RoundNr), to=max(four$RoundNr),
length.out=10)
lines(x=plot.xvals, y=boot.res$ci.predicted$fitted,
lty=2)
lines(x=plot.xvals, y=boot.res$ci.predicted$lower.cl,
lty=3)
lines(x=plot.xvals, y=boot.res$ci.predicted$upper.cl,
lty=3)
```


```{r}
five <- subset(Scrambled.valid.T1, Midtesting_age_group == "5" |Midtesting_age_group == "6")
#we z-transform age 
five$z.age.midtesting=as.vector(scale(five$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(five$z.age.midtesting)#check whether it has worked
sd(five$z.age.midtesting)

five$z.round=as.vector(scale(five$RoundNr))
mean(five$z.round)#check whether it has worked
sd(five$z.round)

library(lme4)
res2<-glmer(Correct ~ z.round + (1|ID), data=five, family = binomial)#singular fit

null<-glmer(Correct ~ 1 + (1|ID), data=five, family = binomial)#singular fit

anova(null, res2, test="Chisq")


boot.res=boot.glmm.pred(model.res=res2, excl.warnings=T,
nboots=1000, para=F, resol=10, use="z.round")
boot.res$ci.estimates
boot.res$ci.predicted

par(mar=c(3, 3, 0.2, 0.2), mgp=c(1.7, 0.3, 0), las=1, tcl=-0.15)
plot(x=five$RoundNr, y=five$Correct, pch=19, las=2, ylim=c(0, 1),
xlab="Trial number", ylab="Probability of success", main = "5-year-olds")
plot.xvals=seq(from=min(five$RoundNr), to=max(five$RoundNr),
length.out=10)
lines(x=plot.xvals, y=boot.res$ci.predicted$fitted,
lty=2)
lines(x=plot.xvals, y=boot.res$ci.predicted$lower.cl,
lty=3)
lines(x=plot.xvals, y=boot.res$ci.predicted$upper.cl,
lty=3)
```


# Trial 2
## Total number of rounds administered
```{r}
Scrambled.valid.SecondTrialFirstRound <- subset(Scrambled.valid, Trial =="2" & RoundNr =="1")

mean(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds)
sd(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds)
min(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds)
max(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds)

tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.SecondTrialFirstRound$TotalNr_Rounds, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 2, the total number of administered trials was 9.75 (SD = 1.27, range 8-11).

- 3y: 10.12 (SD = 1.16, range 8-11)
- 4y: 9.59 (SD = 1.24, range 8-11)
- 3y: 8.31 (SD = 0.85, range 8-11)
- 3y: 11

- Edinburgh: 9.86 (SD = 1.24, range 8-11)
- Fife: 9.68 (SD = 1.28, range 8-11)

- young: 10.09 (SD = 1.18, range 8-11)
- old: 9.41 (SD = 1.27, 8-11)

## Emptied all boxes
```{r}
table(Scrambled.valid.SecondTrialFirstRound$emptied_all_boxes)

table(Scrambled.valid.SecondTrialFirstRound$emptied_all_boxes, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group)

table(Scrambled.valid.SecondTrialFirstRound$emptied_all_boxes, Scrambled.valid.SecondTrialFirstRound$TestingLocation)

table(Scrambled.valid.SecondTrialFirstRound$emptied_all_boxes, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample)
```
125 children (68%) emptied all boxes, 59 did not.

- 3y: 46 yes (55%), 38 no
- 4y: 66 yes (77%), 20 no
- 5y: 13 yes (100%)
- 6y: 0 yes 

- Edinburgh: 47 yes (66%), 24 no
- Fife: 78 yes (69%), 35 no

- young: 53 yes (57%), 40 no
- old: 72 yes (79%), 19 no

## Number of boxes emptied
```{r}
mean(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied)
sd(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied)
min(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied)
max(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied)

tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.SecondTrialFirstRound$NrBoxesEmptied, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 2, the total number of emptied boxes was 7.59 (SD = 0.65, range 5-8).

- 3y: 7.42 (SD = 0.70, range 6-8)
- 4y: 7.71 (SD = 0.61, range 5-8)
- 5y: 8.00 (SD = 0)
- 6y: 7

- Edinburgh: 7.60 (SD = 0.60, range 6-8)
- Fife: 7.58 (SD = 0.69, range 5-8)

- young: 7.45 (SD = 0.68, range 6-8)
- old: 7.74 (SD = 0.59, range 5-8)

## Effiency
```{r}
mean(Scrambled.valid.SecondTrialFirstRound$Efficiency)
sd(Scrambled.valid.SecondTrialFirstRound$Efficiency)
min(Scrambled.valid.SecondTrialFirstRound$Efficiency)
max(Scrambled.valid.SecondTrialFirstRound$Efficiency)

shapiro.test(Scrambled.valid.SecondTrialFirstRound$Efficiency)
hist(Scrambled.valid.SecondTrialFirstRound$Efficiency,
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, max)

tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.SecondTrialFirstRound$Efficiency, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, max)
```
In trial 2, mean efficiency was 0.80 (SD = 0.15, range 0.45-1).

- 3y: 0.75 (SD = 0.15, range 0.54-1)
- 4y: 0.82 (SD = 0.15, range 0.45-1)
- 5y: 0.97 (SD = 0.08, range 0.73-1)
- 6y: 0.63

- Edinburgh: 0.79 (SD = 0.15, range 0.54-1)
- Fife: 0.80 (SD = 0.16, range 0.45-1)

- young: 0.75 (SD = 0.15, range 0.54-1)
- old: 0.84 (SD = 0.15, range 0.45-1)

## For those children wo did make an error, how many correct trials did they have before the first error occurred?
```{r}
Scrambled.valid.SecondTrialFirstRound.mademistake <- subset(Scrambled.valid.SecondTrialFirstRound, NoSearches_before_FirstError != "no error")

mean(Scrambled.valid.SecondTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
sd(Scrambled.valid.SecondTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
min(Scrambled.valid.SecondTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
max(Scrambled.valid.SecondTrialFirstRound.mademistake$NoSearches_before_FirstError_numeric)
```
136 children made an error. Those children had an average of 5.16 (SD = 1.70, range 1-7) rounds correct before making the first error.

## Efficiency when disregarding the first trial 
So that efficiency could also be 0
```{r}
mean(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch)
sd(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch)
min(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch)
max(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch)

shapiro.test(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch)
hist(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch,
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, min)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Midtesting_age_group, max)

threeandfour <- subset(Scrambled.valid.SecondTrialFirstRound, Midtesting_age_group =="3"| Midtesting_age_group =="4")
wilcox.test(threeandfour$EfficiencyDisregardingFirstSearch ~ threeandfour$Midtesting_age_group, alternative = "less")

tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$TestingLocation, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$TestingLocation, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$TestingLocation, min)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$TestingLocation, max)

tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, mean)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, sd)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, min)
tapply(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch, Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, max)

wilcox.test(Scrambled.valid.SecondTrialFirstRound$EfficiencyDisregardingFirstSearch ~ Scrambled.valid.SecondTrialFirstRound$Mediansplit_midtesting_entiresample, alternative = "greater")
```
In trial 2, mean efficiency was 0.78 (SD = 0.17, range 0.40-1).

- 3y: 0.72 (SD = 0.16, range 0.5-1)
- 4y: 0.80 (SD = 0.16, range 0.4-1)
- 5y: 0.97 (SD = 0.09, range 0.7-1)
- 6y: 0.60

- Edinburgh: 0.77 (SD = 0.16, range 0.5-1)
- Fife: 0.78 (SD = 0.17, range 0.4-1)

- young: 0.73 (SD = 0.16, range 0.5-1)
- old: 0.82 (SD = 0.17, range 0.4-1)

## Can Success be predicted by age?
```{r}
Scrambled.valid.T2 <- subset(Scrambled.valid, Trial == "2" & RoundNr !="1")
#we z-transform age 
Scrambled.valid.T2$z.age.midtesting=as.vector(scale(Scrambled.valid.T2$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(Scrambled.valid.T2$z.age.midtesting)#check whether it has worked
sd(Scrambled.valid.T2$z.age.midtesting)

Scrambled.valid.T2$z.round=as.vector(scale(Scrambled.valid.T2$RoundNr))
mean(Scrambled.valid.T2$z.round)#check whether it has worked
sd(Scrambled.valid.T2$z.round)

library(lme4)
res<-glmer(Correct ~ z.age.midtesting + z.round + z.age.midtesting:z.round + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

null<-glmer(Correct ~ 1 + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

anova(null, res, test="Chisq")
```
Together, trial number, age, and the interaction explain the data better than a null model, X2(3) = 380.76, p < .001.

```{r}
res.nointer<-glmer(Correct ~ z.age.midtesting + z.round + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

anova(res.nointer, res, test="Chisq")
```
The interaction term has no effect, X2(1) = 0.134, p = .713.

Remove interaction term from model
```{r}
res<-glmer(Correct ~ z.age.midtesting + z.round + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

null<-glmer(Correct ~ 1 + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

anova(null, res, test="Chisq")
```
Together, trial number and age explain the data better than a null model, X2(2) = 380.63, p < .001.

Effect of age 
```{r}
res.noage<-glmer(Correct ~ z.round + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

anova(res.noage, res, test="Chisq")
```
Age has a significant effect, X2(1) = 17.639, p < .001.

Effect of round number 
```{r}
res.notrial<-glmer(Correct ~ z.age.midtesting + (1|ID), data=Scrambled.valid.T2, family = binomial)#singular fit

anova(res.notrial, res, test="Chisq")
```
Round number has a significant effect, X2(1) = 357.81, p < .001.

## Plot age as continuous variable against efficiency
```{r}
library(ggplot2)
p1<- ggplot(Scrambled.valid.SecondTrialFirstRound, aes(x=Midtesting_age_months, y=EfficiencyDisregardingFirstSearch)) + geom_point()

p1 +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
```

Effect of trial number
```{r}
boot.res=boot.glmm.pred(model.res=res, excl.warnings=T,
nboots=1000, para=F, resol=10, use="z.round")
boot.res$ci.estimates
boot.res$ci.predicted

par(mar=c(3, 3, 0.2, 0.2), mgp=c(1.7, 0.3, 0), las=1, tcl=-0.15)
plot(x=Scrambled.valid.T2$RoundNr, y=Scrambled.valid.T2$Correct, pch=19, las=2, ylim=c(0, 1),
xlab="Trial number", ylab="Probability of success")
plot.xvals=seq(from=min(Scrambled.valid.T2$RoundNr), to=max(Scrambled.valid.T2$RoundNr),
length.out=10)
lines(x=plot.xvals, y=boot.res$ci.predicted$fitted,
lty=2)
lines(x=plot.xvals, y=boot.res$ci.predicted$lower.cl,
lty=3)
lines(x=plot.xvals, y=boot.res$ci.predicted$upper.cl,
lty=3)
```