---
title: "CFA_Children_Blavaan"
author: "Eva Reindl"
date: "20 8 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#Load packages
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(ggpubr)
library(corrr)
library(reshape2)
library(psych)
library(summarytools)
library(lavaan)
library(MVN)
library(car)
library(lavaanPlot)
library(blavaan)
```
# Selection of task DVs
* All DVs have been scaled to values between 0 and 1 with higher values indicating better performance.
* Inhibition tasks: proportion correct searches in *first trial*. 
First trial performance shows signature of prepotent response. Comparability to chimpanzees with first session.
* Shifting tasks: Shifting Boxes: Proportion correct in the CD phase (as measure of susceptibility to interference from anonther stimulus dimension); Shifting Shelf task:  proportion of platform switches; Shifting Trays task: proportion correct. 
* Working memory: WM Boxes and WM Updating (both platforms): proportion of correct choices; WM Grid: proximity of first choice to the baited compartment (ranging between 0 and 1). DVs capture the test performance (in the presence of a secondary task).

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
CFA <-read.csv("CombinedFile_CFA.csv",header=TRUE, sep = ";")
```

# We scale the variables according to testing location
```{r}
Edi <- subset(CFA, TestingLocation == "Edinburgh")
Fife <- subset(CFA, TestingLocation == "Fife")
Edi$WMUpdating <- scale(Edi$WMUpdating)
Edi$WMBoxes <- scale(Edi$WMBoxes)
Edi$WMGrid <- scale(Edi$WMGrid)
Edi$CD_all <- scale(Edi$CD_all)
Edi$Tray <- scale(Edi$Tray)
Edi$Shelf <- scale(Edi$Shelf)
Edi$GlassCeiling <- scale(Edi$GlassCeiling)
Edi$Cylinder <- scale(Edi$Cylinder)
Edi$InhibGrid <- scale(Edi$InhibGrid)

#check whether it has worked
mean(Edi$WMUpdating)
sd(Edi$WMUpdating)

mean(Edi$WMBoxes, na.rm =T)
sd(Edi$WMBoxes, na.rm =T)

mean(Edi$WMGrid, na.rm =T)
sd(Edi$WMGrid, na.rm =T)

mean(Edi$CD_all, na.rm =T)
sd(Edi$CD_all, na.rm =T)

mean(Edi$Tray, na.rm =T)
sd(Edi$Tray, na.rm =T)

mean(Edi$Shelf, na.rm =T)
sd(Edi$Shelf, na.rm =T)

mean(Edi$GlassCeiling, na.rm =T)
sd(Edi$GlassCeiling, na.rm =T)

mean(Edi$Cylinder, na.rm =T)
sd(Edi$Cylinder, na.rm =T)

mean(Edi$InhibGrid, na.rm =T)
sd(Edi$InhibGrid, na.rm =T)


Fife$WMUpdating <- scale(Fife$WMUpdating)
Fife$WMBoxes <- scale(Fife$WMBoxes)
Fife$WMGrid <- scale(Fife$WMGrid)
Fife$CD_all <- scale(Fife$CD_all)
Fife$Tray <- scale(Fife$Tray)
Fife$Shelf <- scale(Fife$Shelf)
Fife$GlassCeiling <- scale(Fife$GlassCeiling)
Fife$Cylinder <- scale(Fife$Cylinder)
Fife$InhibGrid <- scale(Fife$InhibGrid)

CFA_new <- rbind(Fife, Edi)
```  

# Assumptions
```{r}
library(plyr)
library(psych)
multi.hist(CFA_new[-1: -6])
``` 


# Entire sample, including children with missing values
```{r}
model.3factors <- 'F1_WM =~  WMUpdating + WMBoxes + WMGrid
                F2_Shifting =~  CD_all + Shelf + Tray
                  F3_Inhibition =~ Cylinder + InhibGrid + GlassCeiling'

bfit.3factors = bcfa(model.3factors, data = CFA_new, orthogonal=FALSE, adapt = 500, burnin = 2500, sample = 5000, n.chains = 4, control=list(adapt_delta=0.95), bcontrol=list(cores=4))
    return(bfit.3factors)


fit_model = function(model) {
    fit = bcfa(model, data = CFA_new, orthogonal=TRUE, adapt = 500, burnin = 2500, sample = 5000, n.chains = 4, control=list(adapt_delta=0.95), bcontrol=list(cores=4))
    return(fit)
}


model.9factors <- 'F1 =~  WMUpdating
              F2 =~  WMBoxes
              F3 =~  WMGrid
              F4 =~  CD_all
              F5 =~  Shelf
              F6 =~  Tray
              F7 =~  InhibGrid
              F8 =~  Cylinder
              F9 =~  GlassCeiling'

model.MF2012 <- 'F1_WM =~  WMUpdating   + WMBoxes + WMGrid
                F2_Shifting =~  CD_all + Shelf + Tray
                F3_CommonEF =~  Cylinder + InhibGrid + GlassCeiling + Shelf + CD_all + Tray + WMUpdating+ WMBoxes + WMGrid'

model.1factor <- 'F1_CommonEF =~  Cylinder + GlassCeiling + InhibGrid + Shelf + CD_all + Tray + WMUpdating+ WMBoxes + WMGrid'

model.3factors_ind <- 'F1_WM =~  WMUpdating + WMBoxes + WMGrid
                F2_Shifting =~  CD_all + Shelf + Tray
                  F3_Inhibition =~ Cylinder + InhibGrid + GlassCeiling'

model.2factors1 <- 'F1_2_WM_Shifting =~  WMUpdating + WMBoxes + WMGrid+ CD_all + Shelf + Tray
                   F3_Inhibition =~ Cylinder + InhibGrid + GlassCeiling'

model.2factors2 <- 'F1_3_WM_Inh =~  WMUpdating + WMBoxes + WMGrid + InhibGrid + Cylinder + GlassCeiling
                    F2_Shifting =~  CD_all + Shelf + Tray'

model.2factors3 <- 'F1_WM =~  WMUpdating + WMBoxes + WMGrid
                    F2_3_Shifting_Inh=~ CD_all + Shelf + Tray + InhibGrid + Cylinder + GlassCeiling'






# Fit each of the models
bfit.9factors = fit_model(model.9factors)
bfit.MF2012 = fit_model(model.MF2012)
bfit.1factor = fit_model(model.1factor)
bfit.3factors_ind = fit_model(model.3factors_ind)
bfit.2factors1 = fit_model(model.2factors1)
bfit.2factors2 = fit_model(model.2factors2)
bfit.2factors3 = fit_model(model.2factors3)
```  

# Compare models to the 9 factor model
## MF2012
```{r}
blavCompare(bfit.9factors, bfit.MF2012)
``` 

##3 factors
```{r}
blavCompare(bfit.9factors, bfit.3factors)
``` 

## 1 factor
```{r}
blavCompare(bfit.9factors, bfit.1factor)
``` 

## 3 independent factors
```{r}
blavCompare(bfit.9factors, bfit.3factors_ind)
``` 

## 2 factors (WM+Shifting, Inhibition)
```{r}
blavCompare(bfit.9factors, bfit.2factors1)
``` 


## 2 factors (WM+Inhibition, Shifting)
```{r}
blavCompare(bfit.9factors, bfit.2factors2)
``` 

## 2 factors (Inhibition + Shifting, WM)
```{r}
blavCompare(bfit.9factors, bfit.2factors3)
``` 

# Calculate WAIC values for the models
```{r}
get_waic = function(object1) {
    lavopt1 <- object1@Options
    lavopt1$estimator <- "ML"
    ll1 = case_lls(object1@external$mcmcout, object1@Model, 
        object1@ParTable, object1@SampleStats, lavopt1, object1@Cache, 
        object1@Data, make_mcmc(object1@external$mcmcout))
    return(waic(ll1))
}
environment(get_waic) <- asNamespace('blavaan')
get_waic(bfit.9factors)
get_waic(bfit.MF2012)
get_waic(bfit.3factors)
get_waic(bfit.1factor)
get_waic(bfit.3factors_ind)
get_waic(bfit.2factors1)
get_waic(bfit.2factors2)
get_waic(bfit.2factors3)
``` 

# Get fit measures
```{r}
fm.MF2012<-fitMeasures(bfit.MF2012)
fm.3factors<-fitMeasures(bfit.3factors)
fm.1factor<-fitMeasures(bfit.1factor)
fm.3factors_ind<-fitMeasures(bfit.3factors_ind)
fm.2factors1<-fitMeasures(bfit.2factors1)
fm.2factors2<-fitMeasures(bfit.2factors2)
fm.2factors3<-fitMeasures(bfit.2factors3)
fm.9factors<-fitMeasures(bfit.9factors)
``` 

# Put fit measures into a table
```{r}
rbind(fm.MF2012, fm.3factors, fm.3factors_ind,  fm.1factor, fm.2factors1, fm.2factors2, fm.2factors3, fm.9factors)
```

# Summaries for all models
## MF 2012
```{r}
summary(bfit.MF2012, neff=TRUE)
```

## 3 factors
```{r}
summary(bfit.3factors, neff=TRUE)
```

## 1 factor
```{r}
summary(bfit.1factor, neff=TRUE)
```

## 3 independent factors
```{r}
summary(bfit.3factors_ind)
```

## 2 factors (WM+Shifting, Inhibition)
```{r}
summary(bfit.2factors1)
```

## 2 factors (WM+Inhibition, Shifting)
```{r}
summary(bfit.2factors2)
```

## 2 factors (Inhibition + Shifting, WM)
```{r}
summary(bfit.2factors3)
```

## 9 factors
```{r}
summary(bfit.9factors)
```

# Take a look at the effective sample sizes by looking at the underlying stan object
highlights which parameters have a small effective sample size (and how small it is)

## bfit.MF2012
```{r}
tmp1 = blavInspect(bfit.MF2012, "mcobj")
summary(tmp1)
```

## bfit.3factors
```{r}
tmp2 = blavInspect(bfit.3factors, "mcobj")
summary(tmp2)
```

## bfit.1factor
```{r}
tmp3 = blavInspect(bfit.1factor, "mcobj")
summary(tmp3)
```

## bfit.3factors_ind
```{r}
tmp4 = blavInspect(bfit.3factors_ind, "mcobj")
summary(tmp4)
```

## bfit.2factors1
```{r}
tmp4 = blavInspect(bfit.2factors1, "mcobj")
summary(tmp4)
```

## bfit.2factors2
```{r}
tmp5 = blavInspect(bfit.2factors2, "mcobj")
summary(tmp5)
```

## bfit.2factors3
```{r}
tmp6 = blavInspect(bfit.2factors3, "mcobj")
summary(tmp6)
```

## bfit.9factors
```{r}
tmp7 = blavInspect(bfit.9factors, "mcobj")
summary(tmp7)
```


# Compare models to the 1 factor model
## MF2012
```{r}
blavCompare(bfit.1factor, bfit.MF2012)
``` 

##3 factors
```{r}
blavCompare(bfit.1factor, bfit.3factors)
``` 

## 3 independent factors
```{r}
blavCompare(bfit.1factor, bfit.3factors_ind)
``` 

## 2 factors (WM+Shifting, Inhibition)
```{r}
blavCompare(bfit.1factor, bfit.2factors1)
``` 


## 2 factors (WM+Inhibition, Shifting)
```{r}
blavCompare(bfit.1factor, bfit.2factors2)
``` 

## 2 factors (Inhibition + Shifting, WM)
```{r}
blavCompare(bfit.1factor, bfit.2factors3)
``` 


# Plots

p_value = 2*(1-pnorm(abs(MEAN/SE))) 