---
title: "ToolUse"
author: "Eva Reindl"
date: "10 8 2020"
output: html_document
always_allow_html: yes

---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Links <-read.csv("Links_new.csv",header=TRUE, sep = ";")
names(Links)[1] <- "Source"
```

```{r}
library(networkD3)
library(dplyr)

nodes <- data.frame(
  name=c(as.character(Links$Source), 
  as.character(Links$Target)) %>% unique()
)

Links$IDsource <- match(Links$Source, nodes$name)-1 
Links$IDtarget <- match(Links$Target, nodes$name)-1


sankeyNetwork(Links = Links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "Value", NodeID = "name", 
              sinksRight=FALSE)
```


```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Tool <-read.csv("Tool.csv",header=TRUE, sep = ";")
names(Tool)[1] <- "ID"
```
There were 84 children in the dataset.

# Dropouts
```{r}
Tool.dropout <- subset(Tool, Dropout =="yes")
```
There were **9 dropouts** (6 3-year-olds, 1 4-year-olds, 2 5-year-olds; 5 m, 4 f).

- 3 children dropped out because of a change in protocol
- 3 children dropped out because of experimenter error (tube/boxes was not firmly fixed on table)
- 1 child dropped out because of experimenter error (table was not standing on a flat surface)
- 1 child dropped out because of experimenter error (testing outside, wind blew into tube and removed reward)
- 1 child was dropped because they did not understand the instructions (bilingual, too poor language skills)

**75 valid datapoints** are remaining. 

# Description of dataset
## Gender
```{r}
Tool.valid <- subset(Tool, Dropout =="no")
table(Tool.valid$Gender)
```
There are 49 girls and 26 boys.

## Age
### Age at the beginning of testing
```{r}
mean(Tool.valid$Age_months)
sd(Tool.valid$Age_months)
min(Tool.valid$Age_months)
max(Tool.valid$Age_months)
hist(Tool.valid$Age_months)

table(Tool.valid$Age_group)
```
At the beginning of testing, the 75 children were 48.23 (SD = 7.32, range 35-70) months old. There were 1 2-year-old, 35 3-year-olds, 34 4-year-olds, and 5 5-year-olds.

### Age in the middle of testing
```{r}
mean(Tool.valid$MidtestingAgeMonths)
sd(Tool.valid$MidtestingAgeMonths)
min(Tool.valid$MidtestingAgeMonths)
max(Tool.valid$MidtestingAgeMonths)
hist(Tool.valid$MidtestingAgeMonths)

table(Tool.valid$MidtestingAgeGroup)
```
In the middle of testing, the 75 children were 49.84 (SD = 7.34, range 36-72) months old. There were 34 3-year-olds, 33 4-year-olds, 7 5-year-olds, and 1 6-year-old.

### Mediansplit age (based on entire sample)
```{r}
table(Tool.valid$Mediansplit_midtesting_entiresample)
```
There were 36 young and 39 old children.

## Testing location
All children were from the Fife area.

# Score
```{r}
mean(Tool.valid$Score, na.rm = T)
sd(Tool.valid$Score, na.rm = T)
min(Tool.valid$Score, na.rm = T)
max(Tool.valid$Score, na.rm = T)
hist(Tool.valid$Score)

table(Tool.valid$Score)
table(Tool.valid$Score, Tool.valid$MidtestingAgeGroup)
table(Tool.valid$Score, Tool.valid$Mediansplit_midtesting_entiresample)
```
We created scores for all children, including the children with incorrect success, but without those who had incorrect success by blowing out the reward of the tube.
**71 children had a score**:
The mean score was 3.98 (SD = 3.48, range 0-12). The variable was highly left-skewed.

## Ordered logistic regression
```{r}
library(MASS)
Tool.valid$Score <- as.factor(Tool.valid$Score)

#we z-transform age and trial number, as we are including them into an interaction
Tool.valid$z.age=as.vector(scale(Tool.valid$MidtestingAgeMonths))#transform age to mean of 0 and SD of 1
mean(Tool.valid$z.age)#check whether it has worked
sd(Tool.valid$z.age)

Tool.valid$Gender

res <- polr(Score ~ z.age, data = Tool.valid)
null <- polr(Score ~ 1, data = Tool.valid)

anova(null, res, test="Chisq")

#without age z-transformed
res <- polr(Score ~ MidtestingAgeMonths, data = Tool.valid)
null <- polr(Score ~ 1, data = Tool.valid)

anova(null, res, test="Chisq")


```
Age does not significantly contribute to model fit, X2(1) = 2.89, p = .089.

# Plot age as continuous variable against score
```{r}
library(ggplot2)
p1<- ggplot(Tool.valid, aes(x=MidtestingAgeMonths, y=Score)) + geom_point()+
 labs(x="Age in months",y="Score")

p1 +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```


# Success
```{r}
table(Tool.valid$Success)
table(Tool.valid$Success, Tool.valid$MidtestingAgeGroup)
```