---
title: "Smarties"
author: "Eva Reindl"
date: "31 7 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Smarties <-read.csv("Smarties.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(Smarties)[1] <- "ID"
str(Smarties)
```
There are 99 children in the dataset.

# Dropouts
```{r}
dropouts<-subset(Smarties, Dropout == "yes")
```
There are 5 dropouts (4 3-year-olds, 1 4-year-olds; 3 m, 2 f): 

- 1 child did not answer
- 1 child did not stay attentive
- 1 child too poor language skills
- 1 child: experimenter error (did not show child what was inside the box)
- 1 child: answers not understandable

# Valid data
```{r}
Smarties.valid<-subset(Smarties, Dropout == "no")
```
There are **94 valid cases** in the Smarties task.

# Description of sample 
## Gender
```{r}
table(Smarties.valid$Gender)
```
There are **59 females** and **35 males**.

## Age
### Age at the beginning of testing
```{r}
mean(Smarties.valid$Age_months)
sd(Smarties.valid$Age_months)
min(Smarties.valid$Age_months)
max(Smarties.valid$Age_months)

table(Smarties.valid$Age_group)
```
At the beginning of testing, children included in the Smarties task were on average 48.98 months old (SD = 7.43, range 37-70). There were 44 3-year-olds, 42 4-year-olds, and 8 5-year-olds.

### In the middle of testing
```{r}
mean(Smarties.valid$AgeMonths_MidTesting)
sd(Smarties.valid$AgeMonths_MidTesting)
min(Smarties.valid$AgeMonths_MidTesting)
max(Smarties.valid$AgeMonths_MidTesting)
hist(Smarties.valid$AgeMonths_MidTesting)

table(Smarties.valid$AgeGroup_MidTesting)
table(Smarties.valid$AgeGroup_MidTesting, Smarties.valid$Gender)

boys <- subset(Smarties.valid, Gender == "m")
girls <- subset(Smarties.valid, Gender == "f")

hist(boys$AgeMonths_MidTesting)
mean(boys$AgeMonths_MidTesting)
sd(boys$AgeMonths_MidTesting)
min(boys$AgeMonths_MidTesting)
max(boys$AgeMonths_MidTesting)
shapiro.test(boys$AgeMonths_MidTesting)#normally distributed

hist(girls$AgeMonths_MidTesting)
mean(girls$AgeMonths_MidTesting)
sd(girls$AgeMonths_MidTesting)
min(girls$AgeMonths_MidTesting)
max(girls$AgeMonths_MidTesting)
shapiro.test(girls$AgeMonths_MidTesting)#not normally distributed

wilcox.test(Smarties.valid$AgeMonths_MidTesting ~ Smarties.valid$Gender, alternative = "two.sided")
```
In the middle of testing, children included in the Smarties task were on average **50.44 months old (SD = 7.39, range 38-72)**. There were  

- 42 3-year-olds (30f, 12m)
- 40 4-year-olds (22f, 18m)
- 11 5-year-olds (7f, 4m)
- 1 6-year-old (1m)

- Boys: M = 51.68 (SD = 7.76, range 38-72)
- Girls: M = 49.69 (SD = 7.13, range 39-64)

There was no difference between males and females regarding the age distribution, two-sided Wilcoxon test, W = 886.5, p = .254.

### Age mediansplit (based on entire sample)
```{r}
table(Smarties.valid$Mediansplit_midtesting_entiresample)
table(Smarties.valid$Mediansplit_midtesting_entiresample, Smarties.valid$Gender)
```
There were **44 young** (30 f, 14 m) and **50 old** (29 f, 21 m) children.

## Testing Location
All children were from the Fife area.

# Control question 1 (What is inside the box?)
```{r}
table(Smarties.valid$What.is.inside)
```
All 94 children answered the question correctly.

# Test question 1 (What did you think was inside?)
```{r}
table(Smarties.valid$What.did.you.think.was.inside)
table(Smarties.valid$What.did.you.think.was.inside, Smarties.valid$AgeGroup_MidTesting)

threeandfour <- subset(Smarties.valid, AgeGroup_MidTesting =="3" | AgeGroup_MidTesting == "4")
table(threeandfour$What.did.you.think.was.inside, threeandfour$AgeGroup_MidTesting)
chisq.test(threeandfour$What.did.you.think.was.inside, threeandfour$AgeGroup_MidTesting)

table(Smarties.valid$What.did.you.think.was.inside, Smarties.valid$Mediansplit_midtesting_entiresample)

chisq.test(Smarties.valid$What.did.you.think.was.inside, Smarties.valid$Mediansplit_midtesting_entiresample)
```
29 children (31%) answered the question correctly, 65 answered wrongly.

- 3y: 9 correct (21%), 33 wrong
- 4y: 15 correct (37.5%), 25 wrong
- 5y: 4 correct (36%), 7 wrong
- 6y: 1 correct (100%)

There is no difference in performance between 3- and 4-year-olds, X2(1) = 1.839, p = .175.

- young: 9 correct (20%), 35 wrong
- old 20 correct (40%), 30 wrong

There is no difference in performance between young and old children, X(1) = 3.325, p = .068.


# Test question 2 (What did x think is inside the box?)
```{r}
table(Smarties.valid$What.will.x.think.is.inside)
table(Smarties.valid$What.will.x.think.is.inside, Smarties.valid$AgeGroup_MidTesting)

table(threeandfour$What.will.x.think.is.inside, threeandfour$AgeGroup_MidTesting)
chisq.test(threeandfour$What.will.x.think.is.inside, threeandfour$AgeGroup_MidTesting)

table(Smarties.valid$What.will.x.think.is.inside, Smarties.valid$Mediansplit_midtesting_entiresample)

chisq.test(Smarties.valid$What.will.x.think.is.inside, Smarties.valid$Mediansplit_midtesting_entiresample)
```
50 children (53%) answered the question correctly, 44 answered wrongly.

- 3y: 19 correct (59%), 23 wrong
- 4y: 21 correct (51%), 19 wrong
- 5y: 9 correct (36%), 2 wrong
- 6y: 1 correct (100%)

There is no difference in performance between 3- and 4-year-olds, X2(1) = 1.191, p = .662.

- young: 19 correct (43%), 25 wrong
- old: 31 correct (61%), 19 wrong

There is no difference in performance between young and old children, X(1) = 2.616, p = .106.


# Control question 2 (What does box look like?)
```{r}
table(Smarties.valid$What.does.box.look.like)
table(Smarties.valid$What.does.box.look.like, Smarties.valid$AgeGroup_MidTesting)

table(threeandfour$What.does.box.look.like, threeandfour$AgeGroup_MidTesting)
chisq.test(threeandfour$What.does.box.look.like, threeandfour$AgeGroup_MidTesting)

table(Smarties.valid$What.does.box.look.like, Smarties.valid$Mediansplit_midtesting_entiresample)

chisq.test(Smarties.valid$What.does.box.look.like, Smarties.valid$Mediansplit_midtesting_entiresample)
```
40 children (42%) answered the question correctly, 54 answered wrongly.

- 3y: 14 correct (33%), 28 wrong
- 4y: 20 correct (50%), 20 wrong
- 5y: 6 correct (54%), 5 wrong
- 6y: 1 wrong (0%)

There is no difference in performance between 3- and 4-year-olds, X2(1) = 1.708, p = .191.

- young: 14 correct (32%), 30 wrong
- old: 26 correct (52%), 24 wrong

There is no difference in performance between young and old children, X(1) = 3.118, p = .077.


# Control question 3 (What is really inside?)
```{r}
table(Smarties.valid$What.is.really.inside)
table(Smarties.valid$What.is.really.inside, Smarties.valid$AgeGroup_MidTesting)

table(threeandfour$What.is.really.inside, threeandfour$AgeGroup_MidTesting)
chisq.test(threeandfour$What.is.really.inside, threeandfour$AgeGroup_MidTesting)

table(Smarties.valid$What.is.really.inside, Smarties.valid$Mediansplit_midtesting_entiresample)

chisq.test(Smarties.valid$What.is.really.inside, Smarties.valid$Mediansplit_midtesting_entiresample)
```
86 children (91%) answered the question correctly, 8 answered wrongly.

- 3y: 38 correct (90%), 4 wrong
- 4y: 36 correct (90%), 4 wrong
- 5y: 11 correct (100%)
- 6y: 1 correct (100%)

There is no difference in performance between 3- and 4-year-olds.

- young: 40 correct (91%), 4 wrong
- old: 46 correct (92%), 4 wrong

There is no difference in performance between young and old children.

# Score: Own false belief
```{r}
mean(Smarties.valid$Score_OwnFalseBelief)
sd(Smarties.valid$Score_OwnFalseBelief)
min(Smarties.valid$Score_OwnFalseBelief)
max(Smarties.valid$Score_OwnFalseBelief)

table(Smarties.valid$Score_OwnFalseBelief)

tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$AgeGroup_MidTesting, mean)
tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$AgeGroup_MidTesting, sd)
tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$AgeGroup_MidTesting, min)
tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$AgeGroup_MidTesting, max)

table(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$AgeGroup_MidTesting)

three <- subset(Smarties.valid, AgeGroup_MidTesting =="3")
hist(three$Score_OwnFalseBelief)
shapiro.test(three$Score_OwnFalseBelief)#not normally distributed

four <- subset(Smarties.valid, AgeGroup_MidTesting =="4")
hist(four$Score_OwnFalseBelief)
shapiro.test(four$Score_OwnFalseBelief)#not normally distributed

wilcox.test(three$Score_OwnFalseBelief, four$Score_OwnFalseBelief, alternative = "less")

tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, mean)
tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, sd)
tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, min)
tapply(Smarties.valid$Score_OwnFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, max)

young <- subset(Smarties.valid, Mediansplit_midtesting_entiresample =="young")
old <- subset(Smarties.valid, Mediansplit_midtesting_entiresample =="old")
shapiro.test(young$Score_OwnFalseBelief)#not normally distributed
shapiro.test(old$Score_OwnFalseBelief)#not normally distributed

wilcox.test(young$Score_OwnFalseBelief, old$Score_OwnFalseBelief, alternative = "less")

```

0 = at least one control question wrong
1 = control questions correct, test question wrong
2 = control and test questions correct

The average score is 0.57 (SD = 0.80, range 0-2).

- 3y (n = 42): 0.38 (SD = 0.66, range 0-2)
- 4y (n = 40): 0.70 (SD = 0.85, range 0-2)
- 5y (n = 11): 0.91 (SD = 0.94, range 0-2)
- 6y (n = 1): 0

Three-year-olds have a lower score than 4-year-olds, W = 678, p = .040.

- young (n = 44): 0.36 (SD = 0.65, range 0-2)
- old (n = 50): 0.76 (SD = 0.87, range 0-2)

Young children have a lower score than older children, W = 836, p = .011.


# Score: Other false belief
```{r}
mean(Smarties.valid$Score_OtherFalseBelief)
sd(Smarties.valid$Score_OtherFalseBelief)
min(Smarties.valid$Score_OtherFalseBelief)
max(Smarties.valid$Score_OtherFalseBelief)

table(Smarties.valid$Score_OtherFalseBelief)

tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$AgeGroup_MidTesting, mean)
tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$AgeGroup_MidTesting, sd)
tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$AgeGroup_MidTesting, min)
tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$AgeGroup_MidTesting, max)

table(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$AgeGroup_MidTesting)

hist(three$Score_OtherFalseBelief)
shapiro.test(three$Score_OtherFalseBelief)#not normally distributed

hist(four$Score_OtherFalseBelief)
shapiro.test(four$Score_OtherFalseBelief)#not normally distributed

wilcox.test(three$Score_OtherFalseBelief, four$Score_OtherFalseBelief, alternative = "less")

tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, mean)
tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, sd)
tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, min)
tapply(Smarties.valid$Score_OtherFalseBelief, Smarties.valid$Mediansplit_midtesting_entiresample, max)

shapiro.test(young$Score_OtherFalseBelief)#not normally distributed
shapiro.test(old$Score_OtherFalseBelief)#not normally distributed

wilcox.test(young$Score_OtherFalseBelief, old$Score_OtherFalseBelief, alternative = "less")
```

0 = at least one control question wrong
1 = control questions correct, test question wrong
2 = control and test questions correct

The average score is 0.66 (SD = 0.89, range 0-2).

- 3y (n = 42): 0.45 (SD = 0.77, range 0-2)
- 4y (n = 40): 0.80 (SD = 0.94, range 0-2)
- 5y (n = 11): 1.00 (SD = 1.00, range 0-2)
- 6y (n = 1): 0

Three-year-olds have a lower score than 4-year-olds, W = 681, p = .042.

- young (n = 44): 0.43 (SD = 0.76, range 0-2)
- old (n = 50): 0.86 (SD = 0.95, range 0-2)

Young children have a lower score than older children, W = 842, p = .012.


# Total score
```{r}
mean(Smarties.valid$TotalScore)
sd(Smarties.valid$TotalScore)
min(Smarties.valid$TotalScore)
max(Smarties.valid$TotalScore)

tapply(Smarties.valid$TotalScore, Smarties.valid$AgeGroup_MidTesting, mean)
tapply(Smarties.valid$TotalScore, Smarties.valid$AgeGroup_MidTesting, sd)
tapply(Smarties.valid$TotalScore, Smarties.valid$AgeGroup_MidTesting, min)
tapply(Smarties.valid$TotalScore, Smarties.valid$AgeGroup_MidTesting, max)

hist(three$TotalScore)
shapiro.test(three$TotalScore)#not normally distributed

hist(four$TotalScore)
shapiro.test(four$TotalScore)#not normally distributed

wilcox.test(three$TotalScore, four$TotalScore, alternative = "less")

tapply(Smarties.valid$TotalScore, Smarties.valid$Mediansplit_midtesting_entiresample, mean)
tapply(Smarties.valid$TotalScore, Smarties.valid$Mediansplit_midtesting_entiresample, sd)
tapply(Smarties.valid$TotalScore, Smarties.valid$Mediansplit_midtesting_entiresample, min)
tapply(Smarties.valid$TotalScore, Smarties.valid$Mediansplit_midtesting_entiresample, max)

shapiro.test(young$TotalScore)#not normally distributed
shapiro.test(old$TotalScore)#not normally distributed

wilcox.test(young$TotalScore, old$TotalScore, alternative = "less")
```

The average score is 0.85 (SD = 1.18, range 0-3).

- 3y (n = 42): 0.55 (SD = 0.97, range 0-3)
- 4y (n = 40): 1.05 (SD = 1.28, range 0-3)
- 5y (n = 11): 1.36 (SD = 1.36, range 0-3)
- 6y (n = 1): 0

Three-year-olds have a lower score than 4-year-olds, W = 670.5, p = .034.

- young (n = 44): 0.52 (SD = 0.95, range 0-3)
- old (n = 50): 1.14 (SD = 1.29, range 0-3)

Young children have a lower score than older children, W = 825.5, p = .008.