---
title: "SallyAnn"
author: "Eva Reindl"
date: "5 7 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Sally <-read.csv("SallyAnn.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(Sally)[1] <- "ID"
names(Sally)[18] <- "Score"

str(Sally)
```
There are 104 children in the dataset.

# Dropouts
```{r}
dropouts<-subset(Sally, Dropout == "yes")
```
There are 2 dropouts (3y, m): 

- 1 child had too poor language comprehension (bilingual) and the test did not work with them
- 1 child stopped paying attention and so the experimenter stopped the game (child chose at random)

# Valid data
```{r}
Sally.valid<-subset(Sally, Dropout == "no")
```
There are **102 valid cases** in the Sally Ann task.

# Description of sample 
## Gender
```{r}
table(Sally.valid$Gender)
```
There are **63 females** and **39 males**.

## Age
### Age at the beginning of testing
```{r}
mean(Sally.valid$Age_months)
sd(Sally.valid$Age_months)
min(Sally.valid$Age_months)
max(Sally.valid$Age_months)

table(Sally.valid$Age_group)
```
At the beginning of testing, children included in the Sally Ann task were on average 49.10 months old (SD = 7.62, range 35-70). There were 1 2-year-old, 46 3-year-olds, 45 4-year-olds, and 10 5-year-olds.

### In the middle of testing
```{r}
mean(Sally.valid$AgeMonths_midtesting)
sd(Sally.valid$AgeMonths_midtesting)
min(Sally.valid$AgeMonths_midtesting)
max(Sally.valid$AgeMonths_midtesting)
hist(Sally.valid$AgeMonths_midtesting)

table(Sally.valid$AgeGroup_midtesting)
table(Sally.valid$AgeGroup_midtesting, Sally.valid$Gender)

boys <- subset(Sally.valid, Gender == "m")
girls <- subset(Sally.valid, Gender == "f")

hist(boys$AgeMonths_midtesting)
mean(boys$AgeMonths_midtesting)
sd(boys$AgeMonths_midtesting)
min(boys$AgeMonths_midtesting)
max(boys$AgeMonths_midtesting)
shapiro.test(boys$AgeMonths_midtesting)#normally distributed

hist(girls$AgeMonths_midtesting)
mean(girls$AgeMonths_midtesting)
sd(girls$AgeMonths_midtesting)
min(girls$AgeMonths_midtesting)
max(girls$AgeMonths_midtesting)
shapiro.test(girls$AgeMonths_midtesting)#not normally distributed

wilcox.test(Sally.valid$AgeMonths_midtesting ~ Sally.valid$Gender, alternative = "two.sided")
```
In the middle of testing, children included in the Sally Ann task were on average **50.47 months old (SD = 7.54, range 36-72)**. There were  

- 45 3-year-olds (31 f, 14 m)
- 43 4-year-olds (24 f, 19 m)
- 13 5-year-olds (8 f, 5 m)
- 1 6-year-old (1 m)

- Boys: M = 51.56 (SD = 7.91, range 38-72)
- Girls: M = 49.79 (SD = 7.28, range 36-64)

There was no difference between males and females regarding the age distribution, two-sided Wilcoxon test, W = 1089, p = .338.

### Age mediansplit (based on entire sample)
```{r}
table(Sally.valid$Mediansplit_midtesting_entiresample)
table(Sally.valid$Mediansplit_midtesting_entiresample, Sally.valid$Gender)
```
There were **47 young** (31 f, 16 m) and **55 old** (32 f, 23 m) children.

## Testing Location
All children were from the Fife area.

# Control question 1
"Who is Sally? Who is Ann?"
```{r}
table(Sally.valid$WhoSally_WhoAnn)
table(Sally.valid$WhoSally_WhoAnn, Sally.valid$AgeGroup_midtesting)
```
Out of the 102 children, **100 children (98%) passed the first control question**. Note that the experimenter repeated the explanation and the questions up to 3 times, so not all of the children passed the question the first time.

# Test question
"Where will Sally look for her block?"
```{r}
table(Sally.valid$Where.Sally.look)
table(Sally.valid$Where.Sally.look, Sally.valid$AgeGroup_midtesting)

threeandfour <- subset(Sally.valid, AgeGroup_midtesting == "3" | AgeGroup_midtesting == "4")

table(threeandfour$Where.Sally.look, threeandfour$AgeGroup_midtesting)
chisq.test(threeandfour$Where.Sally.look, threeandfour$AgeGroup_midtesting)

table(Sally.valid$Where.Sally.look, Sally.valid$Mediansplit_midtesting_entiresample)
chisq.test(Sally.valid$Where.Sally.look, Sally.valid$Mediansplit_midtesting_entiresample)
```
Out of the 102 children, **40 children (39%) passed the test question**.

- **3y (n = 45): 14 correct (31%)**
- **4y (n = 43): 17 correct (39%)**
- 5y (n = 13): 8 correct (61%)
- 6y (n = 1): 1 correct (100%)

**3- and 4-year-olds did not differ in their success rates**, Chi-squared test X2(1) = 0.364, p = .546.

- young (n = 47): 14 correct (30%)
- old (n = 55): 26 correct (47%)

**Old children did not perform differently than young children**, Chi-squared test X2(1) = 2.558, p = .110.

# Control question 2
"Where is the block really?"
```{r}
table(Sally.valid$Where.block.really)
table(Sally.valid$Where.block.really, Sally.valid$AgeGroup_midtesting)

table(threeandfour$Where.block.really, threeandfour$AgeGroup_midtesting)
chisq.test(threeandfour$Where.block.really, threeandfour$AgeGroup_midtesting)

table(Sally.valid$Where.block.really, Sally.valid$Mediansplit_midtesting_entiresample)
chisq.test(Sally.valid$Where.block.really, Sally.valid$Mediansplit_midtesting_entiresample)
```
Out of the 102 children, **90 children (88%) passed the second control question**. 

- 3y (n = 45): 38 correct (84%)
- 4y (n = 43): 38 correct (88%)
- 5y (n = 13): 13 correct (100%)
- 6y (n = 1): 1 correct (100%)

No difference between 3- and 4-year-olds, X2(1) = 0.051, p = .821.
No difference between young and old children, X2(1) = 1.476, p = .224.

# Control question 3
"Where was the block in the beginning?"
```{r}
table(Sally.valid$Where.was.block.inbeginning)
table(Sally.valid$Where.was.block.inbeginning, Sally.valid$AgeGroup_midtesting)

table(threeandfour$Where.was.block.inbeginning, threeandfour$AgeGroup_midtesting)
chisq.test(threeandfour$Where.was.block.inbeginning, threeandfour$AgeGroup_midtesting)

table(Sally.valid$Where.was.block.inbeginning, Sally.valid$Mediansplit_midtesting_entiresample)
chisq.test(Sally.valid$Where.was.block.inbeginning, Sally.valid$Mediansplit_midtesting_entiresample)
```
Out of the 102 children, **75 children (73%) passed the third control question**. 

- 3y (n = 45): 25 correct (55%)
- 4y (n = 43): 36 correct (84%)
- 5y (n = 13): 13 correct (100%)
- 6y (n = 1): 1 correct (100%)

4-year-olds were significantly better at this task than 3-year-olds, Chi-squared test X2(1) = 6.931, p = .008.

- young (n = 47): 26 correct (55%)
- old (n = 55): 49 correct (89%)

**Old children were differently better than young children**, Chi-squared test X2(1) = 13.166, p < .001.

# Got at least one control question wrong
```{r}
table(Sally.valid$GotAtLeastOneControlQuestionWrong)
table(Sally.valid$GotAtLeastOneControlQuestionWrong, Sally.valid$AgeGroup_midtesting)
```
Out of the 102 children, 34 children **(33%) got at least one control question wrong** and thus were **excluded from calculating the final score**.

- 3y (n = 45): 25 at least one control question wrong (55%)
- 4y (n = 43): 9 at least one control question wrong (21%)
- 5y (n = 13): 0 at least one control question wrong (0%)
- 6y (n = 1): 0 at least one control question wrong (0%)

# Got test correct but at least one control question wrong
```{r}
table(Sally.valid$GotTestCorrectButAtLeastOneControlWrong)
table(Sally.valid$GotTestCorrectButAtLeastOneControlWrong, Sally.valid$AgeGroup_midtesting)
```
Out of the 102 children, 13 children (13%) got the test question correct but at least one control question wrong.

- 3y (n = 45): 10 got test correct but at least one control question wrong (22%)
- 4y (n = 43): 3 got test correct but at least one control question wrong (7%)
- 5y (n = 13): 0 got test correct but at least one control question wrong (0%)
- 6y (n = 1): 0 got test correct but at least one control question wrong (0%)


# DV: Test correct (yes/no) for those children who have all control questions correct
```{r}
passed.control <- subset(Sally.valid, GotAtLeastOneControlQuestionWrong == "0")
```
Out of the 102 children, **68 children (67%) passed the control question and are included** into the analysis.
```{r}
table(passed.control$Where.Sally.look)
table(passed.control$Where.Sally.look, passed.control$AgeGroup_midtesting)

threeandfour <- subset(passed.control, AgeGroup_midtesting == "3" | AgeGroup_midtesting == "4")

table(threeandfour$Where.Sally.look, threeandfour$AgeGroup_midtesting)
chisq.test(threeandfour$Where.Sally.look, threeandfour$AgeGroup_midtesting)

table(passed.control$Where.Sally.look, passed.control$Mediansplit_midtesting_entiresample)
chisq.test(passed.control$Where.Sally.look, passed.control$Mediansplit_midtesting_entiresample)
```
Out of the 68 children, 27 children **(40%) passed the test question**.

- 3y (n = 20): 4 correct (20%)
- 4y (n = 34): 14 correct (41%)
- 5y (n = 13): 8 correct (61%)
- 6y (n = 1): 1 correct (100%)

**3- and 4-year-olds did not differ** in their success rates, Chi-squared test X2(1) = 1.678, p = .195.

- young (n = 21): 4 correct (19%)
- old (n = 47): 23 correct (49%)

**Old children performed significantly better than young children**, Chi-squared test X2(1) = 4.240, p = .039.

## Plot for age groups
```{r}
library(wesanderson)

Percentage <-read.csv("PassedControl_percentagecorrect.csv",header=TRUE, sep = ";")
names(Percentage)[1] <- "AgeGroup_midtesting"

library(ggplot2)

p<-ggplot(data=Percentage, aes(x=AgeGroup_midtesting, y=Percentage, fill = forcats::fct_rev(Answer))) +
  geom_bar(stat="identity")+ 
  theme_minimal()+
  geom_text(aes(y=labelpos, label=Percentage), vjust=2, 
            color="white", size=3.5)+
  labs(x="Age group in years",y="Perentage of children who answered correctly")
  
p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+ scale_fill_manual(values = wes_palette("IsleofDogs2"), name = "Answer given")
```

## Plot for age by mediansplit
```{r}
Percentage <-read.csv("PassedControl_percentagecorrect_agemediansplit.csv",header=TRUE, sep = ";")
names(Percentage)[1] <- "AgeGroup_midtesting"
library(forcats)

Percentage$AgeGroup_midtesting<-fct_relevel(Percentage$AgeGroup_midtesting, "young")
#changes order of boxplots (young before old)


p<-ggplot(data=Percentage, aes(x=AgeGroup_midtesting, y=Percentage, fill = forcats::fct_rev(Answer))) +
  geom_bar(stat="identity")+ 
  theme_minimal()+
  geom_text(aes(y=labelpos, label=Percentage), vjust=2, 
            color="white", size=3.5)+
  labs(x="Mediansplit age",y="Perentage of children who answered correctly")
  
p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+ scale_fill_manual(values = wes_palette("IsleofDogs2"), name = "Answer given")
```

# Score that includes all children
0 = at least one control question wrong
1 = control questions correct but test question wrong
2 = control questions correct and test question correct
```{r}
table(Sally.valid$Score)
table(Sally.valid$Score, Sally.valid$AgeGroup_midtesting)
table(Sally.valid$Score, Sally.valid$Mediansplit_midtesting_entiresample)

mean(Sally.valid$Score)
sd(Sally.valid$Score)
min(Sally.valid$Score)
max(Sally.valid$Score)

library(MASS)
Sally.valid$Score <- as.factor(Sally.valid$Score)
res <- polr(Score ~ AgeMonths_midtesting, data= Sally.valid)

summary(res)

#make table
(ctable <- coef(summary(res)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = p))

#confidence intervals
(ci <- confint(res))

#getting odds ratios
exp(coef(res))
exp(cbind(OR = coef(res), ci))
```

- 0 points (at least 1 control question wrong): 34 children (33%)
- 1 point (control questions correct, test question wrong): 42 children (41%)
- 2 points (control questions correct, test question correct): 26 children (25%)

3y (n = 45):

- 0 points: 25 (55.5%)
- 1 point: 16 (35.5%)
- 2 points: 4 (9%)

4y (n = 43):

- 0 points: 9 (21%)
- 1 point: 21 (49%)
- 2 points: 13 (30%)

5y (n = 13):

- 0 points: 0
- 1 point: 5 (38.5%)
- 2 points: 8 (61.5%)

6y (n = 1):

- 2 points: 1 (100%)

young (n = 47):

- 0 points: 26 (55.5%)
- 1 point: 17 (36.5%)
2 points: 4 (8%)

old (n = 55):

- 0 points: 8 (14.5%)
- 1 point: 25 (45.5%)
2 points: 22 (40%)

Age has a significant effect on the test score.

## Plot score, age groups
```{r}
Scoreplot <-read.csv("Score.csv",header=TRUE, sep = ";")
names(Scoreplot)[1] <- "AgeGroup_midtesting"
Scoreplot$Score <- as.factor(Scoreplot$Score)

library(ggplot2)

p <- ggplot(Scoreplot, aes(x=Score, y=Percentage, fill=Score)) +
geom_bar(position="dodge", stat="identity") +
    ggtitle("Percentages of scores reached by age group") +
    facet_wrap(~AgeGroup_midtesting) +
    theme(legend.position="none") +
    xlab("Score")+
    ylab("Percentage of children reaching the respective score")

p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```

# Can the score be predicted by the Principal Components?
```{r}

library(MASS)
Sally.valid.PC <- subset(Sally.valid, PC1 != "NA")

Sally.valid.PC$Score <- as.factor(Sally.valid.PC$Score)
res <- polr(Score ~ PC1 + PC2 + AgeMonths_midtesting, data= Sally.valid.PC)

null <- polr(Score ~ 1, data= Sally.valid.PC)

anova(null, res, test="Chisq")

summary(res)
```
Age and the two PC can explain the data better than a null model.

## Effect of age
```{r}
res.noage <- polr(Score ~ PC1 + PC2, data= Sally.valid.PC)

anova(res.noage, res, test="Chisq")
```
Significant effect of age.

## Effect of PC1
```{r}
res.noPCOne <- polr(Score ~ AgeMonths_midtesting + PC2, data= Sally.valid.PC)

anova(res.noPCOne, res, test="Chisq")
```
No effect of PC1.

## Effect of PC2
```{r}
res.noPCTwo <- polr(Score ~ AgeMonths_midtesting + PC1, data= Sally.valid.PC)

anova(res.noPCTwo, res, test="Chisq")
```
No effect of PC2.