---
title: "CFA_Children_FactorChecks"
author: "Eva Reindl"
date: "7 10 2020"
output: word_document
---
```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#Load packages
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(ggpubr)
library(corrr)
library(reshape2)
library(psych)
library(summarytools)
library(lavaan)
library(MVN)
library(car)
library(lavaanPlot)
library(blavaan)
```
# Selection of task DVs
* All DVs have been scaled to values between 0 and 1 with higher values indicating better performance.
* Inhibition tasks: proportion correct searches in *first trial*. 
First trial performance shows signature of prepotent response. Comparability to chimpanzees with first session.
* Shifting tasks: Shifting Boxes: Proportion correct in the CD phase (as measure of susceptibility to interference from anonther stimulus dimension); Shifting Shelf task:  proportion of platform switches; Shifting Trays task: proportion correct. 
* Working memory: WM Boxes and WM Updating (both platforms): proportion of correct choices; WM Grid: proximity of first choice to the baited compartment (ranging between 0 and 1). DVs capture the test performance (in the presence of a secondary task).

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
CFA <-read.csv("CombinedFile_CFA.csv",header=TRUE, sep = ";")
```

# We scale the variables according to testing location
```{r}
Edi <- subset(CFA, TestingLocation == "Edinburgh")
Fife <- subset(CFA, TestingLocation == "Fife")
Edi$WMUpdating <- scale(Edi$WMUpdating)
Edi$WMBoxes <- scale(Edi$WMBoxes)
Edi$WMGrid <- scale(Edi$WMGrid)
Edi$CD_all <- scale(Edi$CD_all)
Edi$Tray <- scale(Edi$Tray)
Edi$Shelf <- scale(Edi$Shelf)
Edi$GlassCeiling <- scale(Edi$GlassCeiling)
Edi$Cylinder <- scale(Edi$Cylinder)
Edi$InhibGrid <- scale(Edi$InhibGrid)

#check whether it has worked
mean(Edi$WMUpdating)
sd(Edi$WMUpdating)

mean(Edi$WMBoxes, na.rm =T)
sd(Edi$WMBoxes, na.rm =T)

mean(Edi$WMGrid, na.rm =T)
sd(Edi$WMGrid, na.rm =T)

mean(Edi$CD_all, na.rm =T)
sd(Edi$CD_all, na.rm =T)

mean(Edi$Tray, na.rm =T)
sd(Edi$Tray, na.rm =T)

mean(Edi$Shelf, na.rm =T)
sd(Edi$Shelf, na.rm =T)

mean(Edi$GlassCeiling, na.rm =T)
sd(Edi$GlassCeiling, na.rm =T)

mean(Edi$Cylinder, na.rm =T)
sd(Edi$Cylinder, na.rm =T)

mean(Edi$InhibGrid, na.rm =T)
sd(Edi$InhibGrid, na.rm =T)


Fife$WMUpdating <- scale(Fife$WMUpdating)
Fife$WMBoxes <- scale(Fife$WMBoxes)
Fife$WMGrid <- scale(Fife$WMGrid)
Fife$CD_all <- scale(Fife$CD_all)
Fife$Tray <- scale(Fife$Tray)
Fife$Shelf <- scale(Fife$Shelf)
Fife$GlassCeiling <- scale(Fife$GlassCeiling)
Fife$Cylinder <- scale(Fife$Cylinder)
Fife$InhibGrid <- scale(Fife$InhibGrid)

CFA_new <- rbind(Fife, Edi)
```  

# Assumptions
```{r}
library(plyr)
library(psych)
multi.hist(CFA_new[-1: -6])
``` 


# Entire sample, including children with missing values
```{r}
fit_model = function(model) {
    fit = bcfa(model, data = CFA_new, orthogonal=TRUE, adapt = 500, burnin = 2500, sample = 5000, n.chains = 4, control=list(adapt_delta=0.95), bcontrol=list(cores=3))
    return(fit)
}


model.WM <- 'F1 =~  WMUpdating + WMBoxes + WMGrid'
model.WM.null <- 'F1 =~  WMUpdating 
                  F2 =~  WMBoxes
                  F3 =~  WMGrid'

model.Inhibition <- 'F1 =~  Cylinder + InhibGrid + GlassCeiling' 
model.Inhibition.null <- 'F1 =~  Cylinder
                          F2 =~ InhibGrid
                          F3 =~ GlassCeiling'                 


model.Shifting <- 'F1 =~  CD_all + Shelf + Tray'
model.Shifting.null <- 'F1 =~ CD_all
                  F2 =~ Shelf
                  F3 =~ Tray'



# Fit each of the models
bfit.model.WM = fit_model(model.WM)
bfit.model.WM.null = fit_model(model.WM.null)
bfit.model.Inhibition = fit_model(model.Inhibition)
bfit.model.Inhibition.null = fit_model(model.Inhibition.null)
bfit.model.Shifting = fit_model(model.Shifting)
bfit.model.Shifting.null = fit_model(model.Shifting.null)
```  


```{r}
save.image("~/CFA_Blavaan_ModelChecks.RData")
```

# Compare models
## WM
```{r}
blavCompare(bfit.model.WM.null, bfit.model.WM)
``` 

## Inhibition
```{r}
blavCompare(bfit.model.Inhibition.null, bfit.model.Inhibition)
```

## Shifting
```{r}
blavCompare(bfit.model.Shifting.null, bfit.model.Shifting)
```

# Calculate WAIC values for the models
```{r}
get_waic = function(object1) {
    lavopt1 <- object1@Options
    lavopt1$estimator <- "ML"
    ll1 = case_lls(object1@external$mcmcout, object1@Model, 
        object1@ParTable, object1@SampleStats, lavopt1, object1@Cache, 
        object1@Data, make_mcmc(object1@external$mcmcout))
    return(waic(ll1))
}
environment(get_waic) <- asNamespace('blavaan')
get_waic(bfit.model.WM)
get_waic(bfit.model.WM.null)
get_waic(bfit.model.Inhibition)
get_waic(bfit.model.Inhibition.null)
get_waic(bfit.model.Shifting)
get_waic(bfit.model.Shifting.null)
``` 

# Get fit measures
```{r}
fm.WM<-fitMeasures(bfit.model.WM)
fm.WM.null<-fitMeasures(bfit.model.WM.null)
fm.Inhibition<-fitMeasures(bfit.model.Inhibition)
fm.Inhibition.null<-fitMeasures(bfit.model.Inhibition.null)
fm.Shifting<-fitMeasures(bfit.model.Shifting)
fm.Shifting.null<-fitMeasures(bfit.model.Shifting.null)
``` 

# Put fit measures into a table
```{r}
rbind(fm.WM, fm.WM.null, fm.Inhibition,  fm.Inhibition.null, fm.Shifting, fm.Shifting.null)
```

# Summaries for all models
## WM
```{r}
summary(bfit.model.WM, neff=TRUE)
```

## WM null
```{r}
summary(bfit.model.WM.null, neff=TRUE)
```

## Inhibition
```{r}
summary(bfit.model.Inhibition, neff=TRUE)
```

## Inhibition.null
```{r}
summary(bfit.model.Inhibition.null, neff=TRUE)
```

## Shifting
```{r}
summary(bfit.model.Shifting, neff=TRUE)
```

## Shifting null
```{r}
summary(bfit.model.Shifting.null, neff=TRUE)
```