---
title: "WM Interference IB Boxes Testbattery"
author: "Eva Reindl"
date: "30 3 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
WM.IB <-read.csv("WM_InterferenceIBShort.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
#recode variables
WM.IB$Age_group <- as.factor(WM.IB$Age_groups)#this converts a variable classified as continuous into a categorical variable
levels(WM.IB$Age_group)

names(WM.IB)[1] <- "ID"

str(WM.IB)
```

# Dropouts
```{r}
WM.dropouts<- subset(WM.IB, dropout == "yes")
```
There is **1 dropout** (ID 13) who did not reach 8 trials in either trial 1 nor 2, so this child will be excluded from any further data analysis.

# Valid data
```{r}
WM.IB.valid<- subset(WM.IB, dropout == "no")
WM.IB.valid.T1 <- subset(WM.IB.valid, Trial == "1")
```
There are **184 children** in the dataset.

# Sample description
## Gender distribution
```{r}
table(WM.IB.valid.T1$Gender)
```
There are 100 females and 84 males.

## Age
### Age at beginning of testing
```{r}
mean(WM.IB.valid.T1$Age_months)
sd(WM.IB.valid.T1$Age_months)
min(WM.IB.valid.T1$Age_months)
max(WM.IB.valid.T1$Age_months)
hist(WM.IB.valid.T1$Age_months)

table(WM.IB.valid.T1$Age_group)
```
Children who contributed to this task were, at the beginning of testing, on average 48.52 months old (SD = 6.97, range 35-70). There were 1 2-year-old, 86 3-year-olds, 89 4-year-olds, and 8 5-year-olds.

## Age in the middle of testing
```{r}
mean(WM.IB.valid.T1$AgeMonths_midtesting)
sd(WM.IB.valid.T1$AgeMonths_midtesting)
min(WM.IB.valid.T1$AgeMonths_midtesting)
max(WM.IB.valid.T1$AgeMonths_midtesting)
hist(WM.IB.valid.T1$AgeMonths_midtesting)

table(WM.IB.valid.T1$AgeGroup_midtesting)
```
Children in this task were on average **49.54 months old (SD = 6.99, range 36-72)** when they were in the middle of the test battery. There were 

- 84 3-year-olds
- 88 4-year-olds
- 11 5-year-olds
- 1 6-year-old

## Age mediansplit
```{r}
table(WM.IB.valid.T1$Mediansplit_midtesting_entiresample)
```
There are **94 young** and **90 old** children.

# Testing location
```{r}
table(WM.IB.valid.T1$TestingLocation)
```
109 children were from Fife, 75 children were from Edinburgh.

# Comparison of performance between trial 1 and 2
We first want to check whether the efficiencies in trial 1 and 2 are comparable. We hereby only focus on the efficiency in the searches 3 til 8 (we cut the search numbers at 8 because 1) this increases comparability with the agpe sample and 2) because these seem the most meaningful trials - more searches just mean that children are guessing. We cut the first 2 searches because those are always correct and thus children could not have an efficiency of 0). 

For this analysis, we will only select those children who have completed both trials (n = 179).
```{r}
WM.IB.valid.T1andT2 <-subset(WM.IB.valid, How_many_trials_valid =="1 and 2")
WM.IB.valid.T1andT2.T1 <- subset(WM.IB.valid.T1andT2, Trial =="1")
WM.IB.valid.T1andT2.T2 <- subset(WM.IB.valid.T1andT2, Trial =="2")
```
**179 children completed both trials**.

## Efficiency for trial 1
```{r}
mean(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
sd(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
min(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
max(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

hist(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

shapiro.test(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)#not normally distributed
```
In trial 1, mean efficiency (searches 3-8) is **.74 (SD = 0.15, range 0.33-1)**.


## Efficiency for trial 2
```{r}
mean(WM.IB.valid.T1andT2.T2$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
sd(WM.IB.valid.T1andT2.T2$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
min(WM.IB.valid.T1andT2.T2$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
max(WM.IB.valid.T1andT2.T2$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

hist(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

shapiro.test(WM.IB.valid.T1andT2.T2$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)#not normally distributed
```
In trial 2, mean efficiency (searches 3-8) is **.72 (SD = 0.17, range 0-1)**.

```{r}
wilcox.test(WM.IB.valid.T1andT2.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1andT2.T2$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, paired = TRUE, alternative = "two.sided")
```
Efficiency in both trials is **not different from each other**, two-sided Wilcoxon test, V = 4195.5, p = .093.

```{r}
#LOAD DATA
WM.IB.wide <-read.csv("WM_forwidedata.csv",header=TRUE, sep = ";")
names(WM.IB.wide)[1] <- "ID"
str(WM.IB.wide)

library(tidyr)
data_wide <- spread(WM.IB.wide, Trial, SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

library(ggpubr)

names(data_wide)[2] <- "Trial1_Efficiency"
names(data_wide)[3] <- "Trial2_Efficiency"

p<-ggpaired(data_wide, cond1 = "Trial1_Efficiency", cond2 = "Trial2_Efficiency",
    fill = "condition", palette = "jco", xlab = "Trial",
  ylab = "Proportion of correct trials")
p + theme(legend.position = "none")

cor.test(data_wide$Trial1_Efficiency, data_wide$Trial2_Efficiency)
```
The **correlation between performance in both trials is r = .23, p = .001**.

The plot is the same as:
```{r}
p1<-  
  ggplot(
  data=WM.IB.wide, aes(x=Trial, y=SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, group=Trial)) +
  geom_boxplot()+
  geom_point(colour = "blue", alpha=0.1)+
  geom_line(aes(group=ID), lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  #xlim(0,2)+
  labs(x="",y="Efficiency in searches 3 to 8")+
  ggtitle("WM IB")+
  geom_hline(yintercept=0.57965, linetype="dashed", color = "red")+
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank())
```
The performance between trial 1 and 2 is not different from each other, but correlation is rather low, i.e., some children get better, some get worse. Therefore, we decide to only use the trial 1 data. Note that there are 5 children who did only do trial 1 anyway.

# Description of performance in trial 1
## Total number of searches
```{r}
#across the sample
mean(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)
sd(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)
min(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)
max(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)

hist(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)
table(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)
quantile(WM.IB.valid.T1$NumberSearches_AcrossPlatforms)

#by age groups
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, mean)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, sd)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, min)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, max)

#by age mediansplit
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, mean)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, sd)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, min)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, max)

#by testing location
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$TestingLocation, mean)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$TestingLocation, sd)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$TestingLocation, min)
tapply(WM.IB.valid.T1$NumberSearches_AcrossPlatforms, WM.IB.valid.T1$TestingLocation, max)
```
The mean number of searches until all stickers were found or the max number of searches was reached was 10.22 (SD = 2.47, range 8-18). 50% of the children needed 10 or fewer searches, and 75% of the children needed 12 or fewer searches.

- 3y (n = 84): M = 10.89 (SD = 2.71, range 8-18)
- 4y (n = 88): M = 9.67 (SD = 2.14, range 8-18)
- 5y (n = 11): M = 9.54 (SD = 1.81, range 8-12)
- 6y (n =1): 10

- young (n = 94): M = 10.69 (SD = 2.66, range 8-18)
- old (n = 90): M = 9.73 (SD = 2.15, range 8-18)

- Edinburgh (n = 75): M = 10.07 (SD = 2.15, range 8-18)
- Fife (n = 109): M = 10.33 (SD = 2.67, range 8-18)

## Emptied all boxes?
```{r}
#across the sample
table(WM.IB.valid.T1$Emptied_all_boxes)

#by age groups
table(WM.IB.valid.T1$Emptied_all_boxes, WM.IB.valid.T1$AgeGroup_midtesting)

#by age mediansplit
table(WM.IB.valid.T1$Emptied_all_boxes, WM.IB.valid.T1$Mediansplit_midtesting_entiresample)

#by testing location
table(WM.IB.valid.T1$Emptied_all_boxes, WM.IB.valid.T1$TestingLocation)
```
Of the 184 children, 70 children (38%) emptied all boxes.

- 3y (n = 84): 28 children (33%) emptied all boxes
- 4y (n = 88): 36 children (41%) emptied all boxes
- 5y (n = 11): 6 children (54%) emptied all boxes
- 6y (n =1): 0

- young (n = 94): 31 children (33%) emptied all boxes
- old (n = 90): 39 children (43%) emptied all boxes

- Edinburgh (n = 75): 28 children (37%) emptied all boxes
- Fife (n = 109): 42 children (38%) emptied all boxes

## Efficiency 
```{r}
#across the sample
mean(WM.IB.valid.T1$Efficiency)
sd(WM.IB.valid.T1$Efficiency)
min(WM.IB.valid.T1$Efficiency)
max(WM.IB.valid.T1$Efficiency)

hist(WM.IB.valid.T1$Efficiency)
quantile(WM.IB.valid.T1$Efficiency)

#by age groups
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$AgeGroup_midtesting, mean)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$AgeGroup_midtesting, sd)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$AgeGroup_midtesting, min)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$AgeGroup_midtesting, max)

#by age mediansplit
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, mean)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, sd)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, min)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, max)

#by testing location
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$TestingLocation, mean)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$TestingLocation, sd)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$TestingLocation, min)
tapply(WM.IB.valid.T1$Efficiency, WM.IB.valid.T1$TestingLocation, max)
```
The mean efficiency in trial 1 was **.75 (SD = .17, range .33-1)**. 50% of the children had an efficiency of 75% or less, and 75% of the children had an efficiency of 87.5% or less.

- 3y (n = 84): **M = .70 (SD = .17, range .41-1)**
- 4y (n = 88): **M = .79 (SD = .15, range .33-1)**
- 5y (n = 11): **M = .81 (SD = .14, range .58-1)**
- 6y (n =1): **.70**

- young (n = 94): **M = .71 (SD = .17, range .41-1)**
- old (n = 90): **M = .79 (SD = .16, range .33-1)**

- Edinburgh (n = 75): M = .75 (SD = .15, range .33-1)
- Fife (n = 109): M = .75 (SD = .18, range .41-1)

## Search strategy
```{r}
#across the sample
table(WM.IB.valid.T1$Strategy)

#by age groups
table(WM.IB.valid.T1$Strategy, WM.IB.valid.T1$AgeGroup_midtesting)

#by age mediansplit
table(WM.IB.valid.T1$Strategy, WM.IB.valid.T1$Mediansplit_midtesting_entiresample)

#by testing location
table(WM.IB.valid.T1$Strategy, WM.IB.valid.T1$TestingLocation)
```
Of the 184 children, 5 children (3%) had a search strategy.

- 3y (n = 84): 1 child (1%) used a strategy
- 4y (n = 88): 3 children (3%) used a strategy
- 5y (n = 11): 1 child (9%) used a strategy
- 6y (n =1): 0

- young (n = 94): 2 children (2%) used a strategy
- old (n = 90): 3 children (3%) used a strategy

- Edinburgh (n = 75): 1 child (1%) used a strategy
- Fife (n = 109): 4 children (4%) used a strategy

## DV: Proportion of correct searches in trial 1 in searches 3-8
```{r}
#across the sample
mean(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
sd(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
min(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
max(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

hist(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="Efficiency in trial 1, searches 3-8", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

shapiro.test(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
quantile(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

wilcox.test(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, mu = 0.57965, alternative = "two.sided")

#by age groups
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, mean)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, sd)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, min)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$AgeGroup_midtesting, max)

three <- subset(WM.IB.valid.T1, AgeGroup_midtesting == "3")
four <- subset(WM.IB.valid.T1, AgeGroup_midtesting == "4")
five <- subset(WM.IB.valid.T1, AgeGroup_midtesting == "5")

hist(three$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="3-year-olds", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(four$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="4-year-olds", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(five$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="5-year-olds", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

shapiro.test(three$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
shapiro.test(four$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
shapiro.test(five$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

wilcox.test(three$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, mu = 0.57965, alternative = "two.sided")
wilcox.test(four$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, mu = 0.57965, alternative = "two.sided")
wilcox.test(five$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, mu = 0.57965, alternative = "two.sided")


#by age mediansplit
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, mean)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, sd)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, min)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$Mediansplit_midtesting_entiresample, max)

young <- subset(WM.IB.valid.T1, Mediansplit_midtesting_entiresample == "young")
old <- subset(WM.IB.valid.T1, Mediansplit_midtesting_entiresample == "old")

hist(young$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="Young children", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(old$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="Old children", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

shapiro.test(young$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
shapiro.test(old$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)

wilcox.test(young$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, mu = 0.57965, alternative = "two.sided")
wilcox.test(old$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, mu = 0.57965, alternative = "two.sided")

#by testing location
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$TestingLocation, mean)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$TestingLocation, sd)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$TestingLocation, min)
tapply(WM.IB.valid.T1$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, WM.IB.valid.T1$TestingLocation, max)

Edi <- subset(WM.IB.valid.T1, TestingLocation == "Edinburgh")
Fife <- subset(WM.IB.valid.T1, TestingLocation == "Fife")

hist(Edi$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="Edinburgh children", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(Fife$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms,
     main="Fife children", 
     xlab="Efficiency", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

shapiro.test(Edi$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
shapiro.test(Fife$SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)
```
The mean efficiency in trial 1, searches 3-8, was .74 (SD = .15, range .33-1). 50% of the children had an efficiency of 67% or less, and 75% of the children had an efficiency of 83% or less. The variable was not normally distributed, W = .873, p < .001.

- 3y (n = 84): M = .71 (SD = .14, range .50-1), not normally distributed, W = .835, p < .001
- 4y (n = 88): M = .77 (SD = .15, range .33-1), not normally distributed, W = .876, p < .001
- 5y (n = 11): M = .79 (SD = .15, range .50-1), normally distributed, W = .899, p = .181
- 6y (n =1): .50

- young (n = 94): M = .72 (SD = .14, range .50-1), not normally distributed, W = .857, p < .001
- old (n = 90): M = .76 (SD = .15, range .33-1), not normally distributed, W = .876, p < .001

- Edinburgh (n = 75): M = .74 (SD = .14, range .33-1), not normally distributed, W = .859, p < .001
- Fife (n = 109): M = .74 (SD = .16, range .50-1), not normally distributed, W = .867, p < .001


Plots
```{r}
#Plot, across ages
library(ggplot2)
p<-  ggplot(
  data=WM.IB.valid.T1, aes(x=rep(1, 184), y=SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)) +
  geom_boxplot(outlier.colour = "black")+
  ylim(0, 1)+
  xlim(0,2)+
  labs(x="",y="Efficiency in trial 1, searches 3-8")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Updating")

p + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) + geom_count()+ geom_hline(yintercept=0.57965, linetype="dashed", color = "red")



#Plot, by age groups
p1<-ggplot(data=WM.IB.valid.T1, aes(x=AgeGroup_midtesting,y=SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)) +
  geom_boxplot(aes(group=AgeGroup_midtesting, fill = as.factor(WM.IB.valid.T1$AgeGroup_midtesting)), outlier.colour = "black") + 
      ylim(0,1)+
  xlim(2.5,6.5)+
  geom_point(alpha=0.3) +
  labs(x="",y="Efficiency in trial 1, searches 3-8")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Updating")

p1  +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1), alpha = 0.5)+
  scale_fill_discrete(name = "Age group midtesting", labels = c("3 years, n = 84", "4 years, n = 88", "5 years, n = 11", "6 years, n = 1"))+
  theme(legend.title = element_blank()) + geom_hline(yintercept=0.57965, linetype="dashed", color = "red")


#Plot, by age mediansplit
library(forcats)

WM.IB.valid.T1$Mediansplit_midtesting_entiresample<-fct_relevel(WM.IB.valid.T1$Mediansplit_midtesting_entiresample, "young")
#changes order of boxplots (young before old)

p1<-  ggplot(
  data=WM.IB.valid.T1, aes(x=rep(1, 184), y=SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, fill = Mediansplit_midtesting_entiresample))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Efficiency in trial 1, searches 3-8")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Updating")

p1 +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_point(pch = 21, position = position_jitterdodge(0,0,1.5)) +
  scale_fill_discrete(name = "Age group midtesting (median split)", labels = c("young (36-49 months), n = 94", "old (50-72 months), n = 90")) +  theme(legend.title = element_blank()) + geom_hline(yintercept=0.57965, linetype="dashed", color = "red")



#Plot, by testing location
p1<-  ggplot(
  data=WM.IB.valid.T1, aes(x=rep(1, 184), y=SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms, fill = TestingLocation))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Efficiency in trial 1, searches 3-8")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("WM Updating")

p1 +  
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_point(pch = 21, position = position_jitterdodge(0,0,1.5)) +
  scale_fill_discrete(name = "Testing location", labels = c("Edinburgh, n = 75", "Fife, n = 109")) + geom_hline(yintercept=0.57965, linetype="dashed", color = "red")
```

## Plot age as continuous variable against proportion correct
```{r}
p1<- ggplot(WM.IB.valid.T1, aes(x=AgeMonths_midtesting, y=SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms)) + geom_point()

p1 +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + geom_hline(yintercept=0.57965, linetype="dashed", color = "red")
```


# Can age predict efficiency?
```{r}
library(lme4)

#we z-transform age 
WM.IB.valid.T1$z.age.midtesting=as.vector(scale(WM.IB.valid.T1$AgeMonths_midtesting))#transform age to mean of 0 and SD of 1
mean(WM.IB.valid.T1$z.age.midtesting)#check whether it has worked
sd(WM.IB.valid.T1$z.age.midtesting)

#Full model
res<-lm(SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms ~ z.age.midtesting, data=WM.IB.valid.T1)

null<-lm(SearchesThreetoEight_Efficiency_InRespectiveTrial_AcrossBothPlatforms ~ 1, data=WM.IB.valid.T1)

anova(null, res, test="Chisq")

source("diagnostic_fcns.r")
diagnostics.plot(res)

max(abs(dffits(res)))
hist(dffits(res))

round(cbind(coefficients(res), coefficients(res)+
t(apply(X=dfbeta(res), MARGIN=2, FUN=range))), 3)

max(cooks.distance(res))

```
Age has only a marginally significant effect on proportion correct, X2(1) = 0.068, p = .081.

```{r}
#Full model
res<-lm(Efficiency ~ z.age.midtesting, data=WM.IB.valid.T1)

null<-lm(Efficiency ~ 1, data=WM.IB.valid.T1)

anova(null, res, test="Chisq")
```
`




