---
title: "Worlds"
author: "Eva Reindl"
date: "31 7 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Worlds <-read.csv("Worlds.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(Worlds)[1] <- "ID"
str(Worlds)
```
There are 85 children in the dataset.


# Dropouts
```{r}
dropouts<-subset(Worlds, Dropout == "yes")
```
There are 5 dropouts (2 3-year-olds, 2 4-year-olds, 1 5-year-old; 1 m, 4 f): 

- 2 children opened two cups simultaneously on the test boards
- 3 times experimenter error (cup was knocked off or a block showed in the test)

# Valid data
```{r}
Worlds.valid<-subset(Worlds, Dropout == "no")
```
There are **80 valid cases** in the Worlds task.

# Description of sample 
## Gender
```{r}
table(Worlds.valid$Gender)
```
There are **48 females** and **32 males**.

## Age
### Age at the beginning of testing
```{r}
mean(Worlds.valid$Age_months)
sd(Worlds.valid$Age_months)
min(Worlds.valid$Age_months)
max(Worlds.valid$Age_months)

table(Worlds.valid$Age_group)
```
At the beginning of testing, children included in the Worlds task were on average 48.19 months old (SD = 7.61, range 35-70). There were 1 2-year-old, 39 3-year-olds, 33 4-year-olds, and 7 5-year-olds.

### In the middle of testing
```{r}
mean(Worlds.valid$AgeMonths_Midtesting)
sd(Worlds.valid$AgeMonths_Midtesting)
table(Worlds.valid$AgeMonths_MidTesting)
summary(Worlds.valid$AgeMonths_Midtesting)

table(Worlds.valid$AgeGroup_Midtesting)
table(Worlds.valid$AgeGroup_Midtesting, Worlds.valid$Gender)

boys <- subset(Worlds.valid, Gender == "m")
girls <- subset(Worlds.valid, Gender == "f")

hist(boys$AgeMonths_Midtesting)
mean(boys$AgeMonths_Midtesting)
sd(boys$AgeMonths_Midtesting)
min(boys$AgeMonths_Midtesting)
max(boys$AgeMonths_Midtesting)
shapiro.test(boys$AgeMonths_Midtesting)#normally distributed

hist(girls$AgeMonths_Midtesting)
mean(girls$AgeMonths_Midtesting)
sd(girls$AgeMonths_Midtesting)
min(girls$AgeMonths_Midtesting)
max(girls$AgeMonths_Midtesting)
shapiro.test(girls$AgeMonths_Midtesting)#normally distributed

t.test(Worlds.valid$AgeMonths_Midtesting ~ Worlds.valid$Gender, alternative = "two.sided")
```
In the middle of testing, children included in the Worlds task were on average **49.75 months old (SD = 7.62, range 36-72)**. There were  

- 38 3-year-olds (24f, 14m)
- 31 4-year-olds (18f, 13m)
- 10 5-year-olds (6f, 4m)
- 1 6-year-old (1m)

- Boys: M = 50.00 (SD = 8.28, range 38-72)
- Girls: M = 49.58 (SD = 7.23, range 36-64)

There was no difference between males and females regarding the age distribution.

### Age mediansplit (based on entire sample)
```{r}
table(Worlds.valid$Mediansplit_midtesting_entiresample)
table(Worlds.valid$Mediansplit_midtesting_entiresample, Worlds.valid$Gender)
```
There were **40 young** (24 f, 16 m) and **40 old** (24 f, 16 m) children.

## Testing Location
All children were from the Fife area.

# How many children switched by themselves?
```{r}
table(Worlds.valid$Switched)
```
**78 children switched, 2 did not**. These two were 4 years old.

# Number of cups flipped before switch
```{r}
mean(Worlds.valid$Testboard.Cupsliftedbeforeswitch)
sd(Worlds.valid$Testboard.Cupsliftedbeforeswitch)
min(Worlds.valid$Testboard.Cupsliftedbeforeswitch)
max(Worlds.valid$Testboard.Cupsliftedbeforeswitch)

table(Worlds.valid$Testboard.Cupsliftedbeforeswitch)

tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$AgeGroup_Midtesting, mean)
tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$AgeGroup_Midtesting, sd)
tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$AgeGroup_Midtesting, min)
tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$AgeGroup_Midtesting, max)

three <- subset(Worlds.valid, AgeGroup_Midtesting == "3")
four <- subset(Worlds.valid, AgeGroup_Midtesting == "4")

shapiro.test(three$Testboard.Cupsliftedbeforeswitch)#not normally distributed
shapiro.test(four$Testboard.Cupsliftedbeforeswitch)#not normally distributed
wilcox.test(three$Testboard.Cupsliftedbeforeswitch, four$Testboard.Cupsliftedbeforeswitch, alternative = "two.sided")


tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$Mediansplit_midtesting_entiresample, mean)
tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$Mediansplit_midtesting_entiresample, sd)
tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$Mediansplit_midtesting_entiresample, min)
tapply(Worlds.valid$Testboard.Cupsliftedbeforeswitch, Worlds.valid$Mediansplit_midtesting_entiresample, max)

young <- subset(Worlds.valid, Mediansplit_midtesting_entiresample == "young")
old <- subset(Worlds.valid, Mediansplit_midtesting_entiresample == "old")

shapiro.test(young$Testboard.Cupsliftedbeforeswitch)#not normally distributed
shapiro.test(old$Testboard.Cupsliftedbeforeswitch)#not normally distributed
wilcox.test(young$Testboard.Cupsliftedbeforeswitch, old$Testboard.Cupsliftedbeforeswitch, alternative = "two.sided")
```
Children switched after an average of **6.46 lifted cups** (SD = 4.10, range 1-10).

- 22 children (**27.5%** out of all children, including the ones who did not switch), **switched after 1 cup**
- 6 after 2 cups
- 2 after 3 cups
- 1 after 5 cups
- 3 after 7 cups
- 2 after 8 cups
- 5 after 9 cups
- **39 (49%) after 10 cups** 

- 3y: 5.53 (SD = 4.08, range 1-10)
- 4y: 7.52 (SD = 3.82, range 1-10)
- 5y: 7.30 (SD = 4.35, range 1-10)
- 6y: 1

**3-year-olds switched after fewer cups than 4-year-olds**, W = 427, p = .038.

- young: 5.75 (SD = 4.09, range 1-10)
- old: 7.17 (SD = 4.03, range 1-10)

**Young and old children did not differ** in the number of cups lifted before they switched, W = 643.5, p = .106.


# Time before switch
```{r}
mean(Worlds.valid$TimeUntilSwitchinSec, na.rm = T)
sd(Worlds.valid$TimeUntilSwitchinSec, na.rm = T)
min(Worlds.valid$TimeUntilSwitchinSec, na.rm = T)
max(Worlds.valid$TimeUntilSwitchinSec, na.rm = T)

tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$AgeGroup_Midtesting, mean, na.rm = T)
tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$AgeGroup_Midtesting, sd, na.rm = T)
tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$AgeGroup_Midtesting, min, na.rm = T)
tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$AgeGroup_Midtesting, max, na.rm = T)

shapiro.test(three$TimeUntilSwitchinSec)#not normally distributed
shapiro.test(four$TimeUntilSwitchinSec)#normally distributed
wilcox.test(three$TimeUntilSwitchinSec, four$TimeUntilSwitchinSec, alternative = "two.sided")


tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$Mediansplit_midtesting_entiresample, mean, na.rm = T)
tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$Mediansplit_midtesting_entiresample, sd, na.rm = T)
tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$Mediansplit_midtesting_entiresample, min, na.rm = T)
tapply(Worlds.valid$TimeUntilSwitchinSec, Worlds.valid$Mediansplit_midtesting_entiresample, max, na.rm = T)
```

Children switched after an average of 46.35 seconds (SD = 38.32, range 2-153).

- 3y: 45.66 (SD = 39.83, range 2-137)
- 4y: 54.62 (SD = 38.94, range 3-153)
- 5y: 29.40 (SD = 23.76, range 4-84)
- 6y: 2

3-year-olds did not switch sooner than 4-year-olds, W = 474, p = .333.

- young: 46.57 (SD = 39.33, range 2-137)
- old: 46.10 (SD = 37.77, range 2-153)

Young and old children do not differ in the time after which they switched.