---
title: "BRIEF-P"
author: "Eva Reindl"
date: "25 8 2020"
output: word_document
---


```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
BRIEF <-read.csv("BRIEF-P.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(BRIEF)[1] <- "ID"
str(BRIEF)
```
115 children contributed data to the BRIEF-P.

# Descriptive statistics
```{r}
table(BRIEF$Midtesting_age_group)
table(BRIEF$Mediansplit_midtesting_entiresample)
table(BRIEF$TestingLocation)
table(BRIEF$TestingLocation, BRIEF$Age_group)
tapply(BRIEF$Midtesting_age_months, BRIEF$TestingLocation, mean)
```
There were 51 3-year-olds, 54 4-year-olds, 9 5-year-olds, and 1 6-year-old. There were 59 young and 56 old children. 
71 children were from Fife, 44 children from Edinburgh.

## Inhibit
```{r}
mean(BRIEF$Inhibit)
sd(BRIEF$Inhibit)
min(BRIEF$Inhibit)
max(BRIEF$Inhibit)
hist(BRIEF$Inhibit)

tapply(BRIEF$Inhibit, BRIEF$Midtesting_age_group, mean)
tapply(BRIEF$Inhibit, BRIEF$Midtesting_age_group, sd)
tapply(BRIEF$Inhibit, BRIEF$Midtesting_age_group, min)
tapply(BRIEF$Inhibit, BRIEF$Midtesting_age_group, max)

tapply(BRIEF$Inhibit, BRIEF$Mediansplit_midtesting_entiresample, mean)
tapply(BRIEF$Inhibit, BRIEF$Mediansplit_midtesting_entiresample, sd)
tapply(BRIEF$Inhibit, BRIEF$Mediansplit_midtesting_entiresample, min)
tapply(BRIEF$Inhibit, BRIEF$Mediansplit_midtesting_entiresample, max)

tapply(BRIEF$Inhibit, BRIEF$TestingLocation, mean)
tapply(BRIEF$Inhibit, BRIEF$TestingLocation, sd)
tapply(BRIEF$Inhibit, BRIEF$TestingLocation, min)
tapply(BRIEF$Inhibit, BRIEF$TestingLocation, max)

Edi <- subset(BRIEF, TestingLocation == "Edinburgh")
Fife <- subset(BRIEF, TestingLocation == "Fife")
shapiro.test(Edi$Inhibit)#not normally distributed
shapiro.test(Fife$Inhibit)#not normally distributed
wilcox.test(BRIEF$Inhibit ~ BRIEF$TestingLocation, alternative = "two.sided")
```
The mean Inhibit score was 51.16 (SD = 11.33, range 34-87).

- 3y (n = 51): 53.31 (SD = 12.06, range 34-85)
- 4y (n = 54): 49.17 (SD = 11.00, range 36-87)
- 5y (n = 51): 51.11 (SD = 7.97, range 43-65)
- 6y (n = 1): 50

- young (n = 59): 52.71 (SD = 11.56, range 34-85)
- old (n = 56): 49.53 (SD = 10.95, range 36-87)

- Fife (n = 71): 53.13 (SD = 11.84, range 36-87)
- Edinburgh (n = 44): 48.00 (SD = 9.78, range 34-78)
Children in Fife have a higher Inhibition score than children in Edinburgh, W = 1150, p = .018.

## Shift
```{r}
mean(BRIEF$Shift)
sd(BRIEF$Shift)
min(BRIEF$Shift)
max(BRIEF$Shift)

tapply(BRIEF$Shift, BRIEF$Midtesting_age_group, mean)
tapply(BRIEF$Shift, BRIEF$Midtesting_age_group, sd)
tapply(BRIEF$Shift, BRIEF$Midtesting_age_group, min)
tapply(BRIEF$Shift, BRIEF$Midtesting_age_group, max)

tapply(BRIEF$Shift, BRIEF$Mediansplit_midtesting_entiresample, mean)
tapply(BRIEF$Shift, BRIEF$Mediansplit_midtesting_entiresample, sd)
tapply(BRIEF$Shift, BRIEF$Mediansplit_midtesting_entiresample, min)
tapply(BRIEF$Shift, BRIEF$Mediansplit_midtesting_entiresample, max)

tapply(BRIEF$Shift, BRIEF$TestingLocation, mean)
tapply(BRIEF$Shift, BRIEF$TestingLocation, sd)
tapply(BRIEF$Shift, BRIEF$TestingLocation, min)
tapply(BRIEF$Shift, BRIEF$TestingLocation, max)

shapiro.test(Edi$Shift)#not normally distributed
shapiro.test(Fife$Shift)#not normally distributed
wilcox.test(BRIEF$Shift ~ BRIEF$TestingLocation, alternative = "two.sided")
```
The mean Shift score was 47.39 (SD = 9.06, range 37-86).

- 3y (n = 51): 48.14 (SD = 11.15, range 37-86)
- 4y (n = 54): 47.09 (SD = 7.29, range 38-64)
- 5y (n = 51): 45.22 (SD = 5.43, range 38-52)
- 6y (n = 1): 45

- young (n = 59): 47.95 (SD = 10.58, range 37-86)
- old (n = 56): 46.80 (SD = 7.16, range 38-64)

- Fife (n = 71): 48.34 (SD = 9.93, range 37-86)
- Edinburgh (n = 44): 45.86 (SD = 7.27, range 37-64)
Children in Fife do not differ in their performance, W = 1361.5, p = .248.

## Working memory
```{r}
mean(BRIEF$WorkingMemory)
sd(BRIEF$WorkingMemory)
min(BRIEF$WorkingMemory)
max(BRIEF$WorkingMemory)

tapply(BRIEF$WorkingMemory, BRIEF$Midtesting_age_group, mean)
tapply(BRIEF$WorkingMemory, BRIEF$Midtesting_age_group, sd)
tapply(BRIEF$WorkingMemory, BRIEF$Midtesting_age_group, min)
tapply(BRIEF$WorkingMemory, BRIEF$Midtesting_age_group, max)

tapply(BRIEF$WorkingMemory, BRIEF$Mediansplit_midtesting_entiresample, mean)
tapply(BRIEF$WorkingMemory, BRIEF$Mediansplit_midtesting_entiresample, sd)
tapply(BRIEF$WorkingMemory, BRIEF$Mediansplit_midtesting_entiresample, min)
tapply(BRIEF$WorkingMemory, BRIEF$Mediansplit_midtesting_entiresample, max)

tapply(BRIEF$WorkingMemory, BRIEF$TestingLocation, mean)
tapply(BRIEF$WorkingMemory, BRIEF$TestingLocation, sd)
tapply(BRIEF$WorkingMemory, BRIEF$TestingLocation, min)
tapply(BRIEF$WorkingMemory, BRIEF$TestingLocation, max)

shapiro.test(Edi$WorkingMemory)#not normally distributed
shapiro.test(Fife$WorkingMemory)#not normally distributed
wilcox.test(BRIEF$WorkingMemory ~ BRIEF$TestingLocation, alternative = "two.sided")
```
The mean WM score was 51.00 (SD = 12.30, range 36-96).

- 3y (n = 51): 52.88 (SD = 12.88, range 36-93)
- 4y (n = 54): 49.17 (SD = 12.15, range 36-96)
- 5y (n = 51): 50.33 (SD = 9.22, range 40-66)
- 6y (n = 1): 60

- young (n = 59): 52.29 (SD = 12.38, range 36-93)
- old (n = 56): 49.64 (SD = 12.17, range 38-96)

- Fife (n = 71): 51.98 (SD = 13.19, range 36-96)
- Edinburgh (n = 44): 49.41 (SD = 10.65, range 36-74)
Children in Fife do not differ in their performance, W = 1408, p = .376.