---
title: "BPVS"
author: "Eva Reindl"
date: "5 5 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
BPVS <-read.csv("BPVS.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(BPVS)[1] <- "ID"
str(BPVS)
```
There are 156 children in the dataset.

# Dropouts
```{r}
BPVS.dropout<-subset(BPVS, Dropout. =="yes")
```
There are **7 dropouts**:

- for 5 children, no basal set could be established. For two of those children, it was suspected that the children answered wrongly on purpose.
- 1 child stopped the game
- for 1 child, the raw score was so low that the standardized score could not be calculated.

# Valid data
```{r}
BPVS.clean<-subset(BPVS, Dropout. =="no")
```
There are **149 children** with valid data.

# Sample description
## Gender distribution
```{r}
table(BPVS.clean$Gender)
```
There are 79 girls and 70 boys.

## Age
### Age at beginning of testing (which was basis for calculation of scores)
```{r}
mean(BPVS.clean$Age_months)
sd(BPVS.clean$Age_months)
min(BPVS.clean$Age_months)
max(BPVS.clean$Age_months)
hist(BPVS.clean$Age_months)
table(BPVS.clean$Age_group)
```
The children who contributed data to the BPVS were on average 49.15 months (SD = 6.82, range 35-70) at the beginning of testing. There were 

- 1 2-year-old (scores caluclated as if child was 3)
- 62 3-year-olds
- 79 4-year-olds
- 7 5-year-olds

### Age in the middle of testing 
```{r}
mean(BPVS.clean$Midtesting_age_months)
sd(BPVS.clean$Midtesting_age_months)
min(BPVS.clean$Midtesting_age_months)
max(BPVS.clean$Midtesting_age_months)
hist(BPVS.clean$Midtesting_age_months)
table(BPVS.clean$Midtesting_age_group)
```
The children who contributed data to the BPVS were on average **50.21 months (SD = 6.77, range 36-72)** in the middle of testing. There were 

- 60 3-year-olds
- 77 4-year-olds
- 10 5-year-olds
- 1 6-year-old

### Mediansplit young/old based on entire sample of test battery children 
median is 49 months, "young" children are <= 49 months, "old" children are >49 months
```{r}
table(BPVS.clean$Mediansplit_midtesting_entiresample)
```
There were **70 young** children and **79 old** children.


# BPVS score
## Across the entire sample
```{r}
mean(BPVS.clean$BPVS_StandardizedScore)
sd(BPVS.clean$BPVS_StandardizedScore)
min(BPVS.clean$BPVS_StandardizedScore)
max(BPVS.clean$BPVS_StandardizedScore)
hist(BPVS.clean$BPVS_StandardizedScore)
shapiro.test(BPVS.clean$BPVS_StandardizedScore)
```
Across the entire sample, the average BPVS standardized score was **104.33 (SD = 12.61, range 77-126)**. The distribution of the variable was bimodal and is not normally distributed, W = 0.959, p < .001.

## By gender
```{r}
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Gender, mean)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Gender, sd)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Gender, min)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Gender, max)
```

- Girls (n = 79): M = 103.71 (SD = 11.98, range 82-126)
- Boys (n = 70): M = 105.03 (SD = 13.34, range 77-126)

## By age groups at midtesting
```{r}
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Midtesting_age_group, mean)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Midtesting_age_group, sd)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Midtesting_age_group, min)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Midtesting_age_group, max)
```

- 3y (n = 60): M = 100.03 (SD = 11.79, range 80-122)
- 4y (n = 77): M = 107.66 (SD = 12.21, range 77-126)
- 5y (n = 10): M = 107.10 (SD = 13.26, range 77-122)
- 6y (n = 1): 94

## By mediansplit age
```{r}
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Mediansplit_midtesting_entiresample, mean)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Mediansplit_midtesting_entiresample, sd)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Mediansplit_midtesting_entiresample, min)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$Mediansplit_midtesting_entiresample, max)
```

- young (n = 70): M = 100.80 (SD = 12.46, range 80-123)
- old (n = 79): M = 107.45 (SD = 11.96, range 77-126)

## By testing location (Edinburgh vs Fife):
```{r}
table(BPVS.clean$TestingLocation)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$TestingLocation, mean)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$TestingLocation, sd)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$TestingLocation, min)
tapply(BPVS.clean$BPVS_StandardizedScore, BPVS.clean$TestingLocation, max)
```

- Edinburgh (n = 67): M = 107.24 (SD = 12.56, range 77-126)
- Fife (n = 82): M = 101.95 (SD = 12.21, range 77-125)

### We then look at the age distribution of Edinburgh and Fife.
```{r}
table(BPVS.clean$TestingLocation, BPVS.clean$Midtesting_age_group)
tapply(BPVS.clean$Midtesting_age_months, BPVS.clean$TestingLocation, mean)
tapply(BPVS.clean$Midtesting_age_months, BPVS.clean$TestingLocation, sd)
tapply(BPVS.clean$Midtesting_age_months, BPVS.clean$TestingLocation, min)
tapply(BPVS.clean$Midtesting_age_months, BPVS.clean$TestingLocation, max)
```

- Edinburgh: 25 3y, 41 4y. M = 49.83 months (SD = 5.83, range 36-58)
- Fife: 35 3y, 36 4y 10 5y, 1 6y. M = 50.52 months (SD = 7.48, range 36-72)


### Can the BPVS score be predicted by testing location, above age?
```{r}
library(lme4)
BPVS.clean$z.age=as.vector(scale(BPVS.clean$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(BPVS.clean$z.age)#check whether it has worked
sd(BPVS.clean$z.age)
res<-lm(BPVS_StandardizedScore ~ z.age + TestingLocation, data = BPVS.clean)
```

#### Check of assumptions
1) Normality of residuals
```{r}
hist(residuals(res), probability=T)

#add line:
x=seq(from=min(residuals(res)),
to=max(residuals(res)), length.out=100)
lines(x=x, y=dnorm(x, mean=0,
sd=sd(residuals(res))))

#a safer option is to look at the qq plot:
qqnorm(residuals(res));qqline(residuals(res))

plot(residuals(res))
```
Not really normal, but only slightly skewed, so probably ok? The qq-plot reveals that large values are too large - see also the histogram.

2) Homogeneity of residuals
```{r}
plot(fitted(res), residuals(res), pch=19)
```
A pattern is visible after all - this might be problematic.

3) Is there a correlation between absolute residuals and fitted values?
```{r}
cor.test(fitted(res), abs(residuals(res)))
```
No, so this seems ok.

4) Influence diagnostics
DFFits
```{r}
dffits(res)
max(abs(dffits(res)))
hist(dffits(res))
plot(dffits(res))
```
DFFit: Values around 2 are reason to worry, but all our values are below 0.5, so this is ok.

DFBetas
```{r}
round(cbind(coefficients(res), coefficients(res)+
t(apply(X=dfbeta(res), MARGIN=2, FUN=range))), 5)

plot(dfbeta(res)[,1])#needs to be done by column
plot(dfbeta(res)[,2])
plot(dfbeta(res)[,3])
```
DFBeta: looks good, little variation.

Cook's distance
```{r}
max(cooks.distance(res))
plot(cooks.distance(res))
```
Cook's distance: values above 1 are reason to worry, but our maximum value is 0.07.


Leverage
```{r}
max(as.vector(influence(res)$hat))
plot(as.vector(influence(res)$hat))

length(coefficients(res))# this is calculating k, which is the number of predictors
2*(3+1)/149 
3*(3+1)/149 
```
Leverage: values > 2*(k+1)/n or > 3*(k+1)/n are a reason to worry (k = number of predictors); in our case the thresholds are 0.05 and 0.08, and our max value is 0.08, so this is just ok.


```{r}
null<-lm(BPVS_StandardizedScore ~ 1, data = BPVS.clean)
anova(null, res, test="Chisq")
summary(res)
drop1(res)
cbind(coefficients(res), confint(res))
```
Together, age in months and testing location can explain the BPVS scores better than a model just containing the intercept, X2(2) = 2621.8, p < .001.
There is a significant effect of age (X2(1) = 1590.9, p = .001) and testing location (X2(1) = 1162.1, p = .005). With each standard deviation increase in age, the BPVS standardized score increases by 3.28 (95% CI [1.34; 5.23])units. When moving from Edinburgh to Fife, the expected score for a child of mean age decreases by 5.62 (95% CI [1.72; 9.52])units.

### Plot the effect of testing location
```{r}
library(ggplot2)

p1<-  ggplot(
  data=BPVS.clean, aes(x=rep(1, 149), y=BPVS_StandardizedScore, fill = TestingLocation))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(60,130)+
  xlim(0,2)+
  labs(x="Testing Location",y="BPVS Standardized Score")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("BPVS Score by Testing Location")

p1 +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1.5), alpha = 0.5) + scale_size_area(max_size=10)+
  scale_fill_discrete(name = "Testing location", labels = c("Edinburgh, n = 67", "Fife, n = 82"))
```

## We further examine the distribution of the standardised score in each testing location subset.
First we create a subset for each testing location.
```{r}
Edi<-subset(BPVS.clean, TestingLocation =="Edinburgh")
Fife<-subset(BPVS.clean, TestingLocation =="Fife")
```

```{r}
hist(Edi$BPVS_StandardizedScore)
shapiro.test(Edi$BPVS_StandardizedScore)#not normally distributed

hist(Fife$BPVS_StandardizedScore)
shapiro.test(Fife$BPVS_StandardizedScore)#not normally distributed

wilcox.test(BPVS.clean$BPVS_StandardizedScore ~ BPVS.clean$TestingLocation, alternative = "greater")
```
For the Fife children, the distribution is bimodal, which is not the case for the Edinburgh children.