---
title: "Foil"
author: "Eva Reindl"
date: "24 4 2020"
output: word_document
---
```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Foil <-read.csv("Foil.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(Foil)[1] <- "ID"
str(Foil)
```
There are 87 children in the dataset. 

# Dropouts
```{r}
Foil.dropout <-subset(Foil, Dropout =="yes")
```
Of the 87 children, there are **6 dropouts** (3 m, 3 f; 3 3-year-olds, 2 4-year-olds, 1 5-year-old):

- 1 child stopped in additional warm-up trials
- 1 child stopped after 4 trials
- 1 child stopped after 5 trials
- 1 child experimenter errors (holes were not of equal size)
- 1 child experimenter error (saw experimenter bait cups through camera)
- 1 child experimenter error (put sticker in wrong cup early)

**81 children are remaining**.

# Valid data
```{r}
Foil.valid.T1 <-subset(Foil, Dropout =="no" & Trial_Nr =="1")
table(Foil.valid.T1$StoppedEarly)
```
These 81 children include 1 child (ID 133) who only received 7 test trials (as tin foil ran out). We decide to include this child as this child completed 75% of test trials.


# Description of sample
## Gender distribution
```{r}
table(Foil.valid.T1$Gender)
```
There were 47 girls and 34 boys.

## Age
### Age at the beginning of testing
```{r}
mean(Foil.valid.T1$Age_months)
sd(Foil.valid.T1$Age_months)
min(Foil.valid.T1$Age_months)
max(Foil.valid.T1$Age_months)

table(Foil.valid.T1$Age_group)

table(Foil.valid.T1$Age_group, Foil.valid.T1$Gender)
```
At the beginning of testing, the children who had valid data on the Foil task were on average 48.37 months (SD = 7.29, range 36-70) old. There were 39 3-year-olds, 36 4-year-olds, and 6 5-year-olds.

- 3y: 24 f, 15 m
- 4y: 21 f, 15 m
- 5y: 2 f, 4 m

### Age in the middle of testing
```{r}
mean(Foil.valid.T1$Midtesting_age_months)
sd(Foil.valid.T1$Midtesting_age_months)
min(Foil.valid.T1$Midtesting_age_months)
max(Foil.valid.T1$Midtesting_age_months)

table(Foil.valid.T1$Midtesting_age_group)

table(Foil.valid.T1$Midtesting_age_group, Foil.valid.T1$Gender)
```
In the middle of testing, the children who had valid data on the Foil task were on average **49.91 months (SD = 7.34, range 38-72)** old. There were **37 3-year-olds, 35 4-year-olds, 8 5-year-olds, and 1 6-year-old**.

- 3y: 24 f, 13 m
- 4y: 19 f, 16 m
- 5y: 4 f, 4 m
- 6y: 1m

### Age mediansplit (based on entire sample)
```{r}
table(Foil.valid.T1$Mediansplit_midtesting_entiresample)

table(Foil.valid.T1$Mediansplit_midtesting_entiresample, Foil.valid.T1$Gender)
```
There were **39 young** and **42 old** children.

- young: 23 f, 19 m
- old: 24 f, 15 m

## Testing location
All children were from the Fife area.

# Criterion reached
```{r}
table(Foil.valid.T1$Warm.up.Crit.reached)
```
Of the 81 children, 4 children (all 3 years old) did not reach the warm-up criterion. 77 children (95%) reached the warm-up criterion.

# Number of administered test trials
```{r}
Foil.valid.T1.critreached<-subset(Foil.valid.T1, Warm.up.Crit.reached =="yes, within 2 trials" | Warm.up.Crit.reached =="yes, within 7 trials")

table(Foil.valid.T1.critreached$Nr.AdministeredTestTrials)
```
76 children were administered 8 trials, 1 child got 7 trials.

# Proportion of correct trials
```{r}
mean(Foil.valid.T1.critreached$ProportionCorrect)
sd(Foil.valid.T1.critreached$ProportionCorrect)
min(Foil.valid.T1.critreached$ProportionCorrect)
max(Foil.valid.T1.critreached$ProportionCorrect)

hist(Foil.valid.T1.critreached$ProportionCorrect)
shapiro.test(Foil.valid.T1.critreached$ProportionCorrect)
wilcox.test(Foil.valid.T1.critreached$ProportionCorrect, mu = 0.5, alternative = "two.sided")

#by age groups
table(Foil.valid.T1.critreached$Midtesting_age_group)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Midtesting_age_group, mean)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Midtesting_age_group, sd)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Midtesting_age_group, min)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Midtesting_age_group, max)

three.years<- subset(Foil.valid.T1.critreached, Midtesting_age_group =="3")
four.years<- subset(Foil.valid.T1.critreached, Midtesting_age_group =="4")
five.years<- subset(Foil.valid.T1.critreached, Midtesting_age_group =="5")

shapiro.test(three.years$ProportionCorrect)
shapiro.test(four.years$ProportionCorrect)
shapiro.test(five.years$ProportionCorrect)

wilcox.test(three.years$ProportionCorrect,mu = 0.5, alternative = "two.sided")
t.test(four.years$ProportionCorrect, mu = 0.5, alternative = "two.sided")
wilcox.test(five.years$ProportionCorrect,mu = 0.5, alternative = "two.sided")

threeandfour <- subset(Foil.valid.T1.critreached, Midtesting_age_group =="3" | Midtesting_age_group =="4")
wilcox.test(threeandfour$ProportionCorrect ~ threeandfour$Midtesting_age_group, alternative = "less")

#by mediansplit
table(Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample, mean)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample, sd)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample, min)
tapply(Foil.valid.T1.critreached$ProportionCorrect, Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample, max)

young<- subset(Foil.valid.T1.critreached, Mediansplit_midtesting_entiresample =="young")
old<- subset(Foil.valid.T1.critreached, Mediansplit_midtesting_entiresample =="old")

shapiro.test(young$ProportionCorrect)
shapiro.test(old$ProportionCorrect)

t.test(young$ProportionCorrect,mu = 0.5, alternative = "two.sided")
wilcox.test(old$ProportionCorrect, mu = 0.5, alternative = "two.sided")

wilcox.test(Foil.valid.T1.critreached$ProportionCorrect ~ Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample, alternative = "greater")
```
Of the 77 children who reached the warm-up criterion in the Foil task, children had on average a proportion of 0.57 (SD = 0.20, range .12-1) test trials correct. This variable is not normally distributed, W = 0.957, p = .010. Performance is significantly above chance, V = 1417.5, p = .004.

- 3y (n = 33): 0.53 (SD = 0.19, range 0.12-0.87), normally distributed, W = 0.954, p = .179, performance at chance, V = 180, p = .387
- 4y (n = 35): 0.55 (SD = 0.20, range 0.25-0.87), not normally distributed, W = 0.913, p = .009, performance at chance, t(34) = 1.502, p = .142
- 5y (n = 8): 0.79 (SD = 0.15, range 0.62-1), normally distributed, W = 0.879, p = .186, performance above chance, V = 36, p = .014
- 6y (n = 1): 0.75

- young (n = 35): 0.54 (SD = 0.19, range 0.12-0.87), normally distributed, W = 0.956, p = .176, performance at chance, t(34) = 1.340, p = .189
- old (n = 42): 0.59 (SD = 0.21, range 0.25-1), not normally distributed, W = 0.939, p = .027, performance above chance, V = 522, p = .009

Boxplot:
```{r}
library(ggplot2)

p<-  ggplot(
  data=Foil.valid.T1.critreached, aes(x=rep(1, 77), y=ProportionCorrect)) +
  geom_boxplot(outlier.colour = "black")+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean proportion of correct trials")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Foil")

p + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") + geom_count()
```


Boxplot:
```{r}
p1<-ggplot(data=Foil.valid.T1.critreached, aes(x=Midtesting_age_group,y=ProportionCorrect)) +
  geom_boxplot(aes(group=Midtesting_age_group, fill = as.factor(Midtesting_age_group)), outlier.colour = "black") + 
      ylim(0,1)+
  xlim(2.5,6.5)+
  geom_point(alpha=0.3) +
  labs(x="",y="Mean proportion correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Foil")

p1 +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  geom_count(colour = "black", position = position_jitterdodge(0,0,1), alpha = 0.5)+
  scale_fill_discrete(name = "Age group midtesting", labels = c("3 years, n = 33", "4 years, n = 35", "5 years, n = 8", "6 years, n = 1"))
```


```{r}
library(forcats)

Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample<-fct_relevel(Foil.valid.T1.critreached$Mediansplit_midtesting_entiresample, "young")
#changes order of boxplots (young before old)

p1<-  ggplot(
  data=Foil.valid.T1.critreached, aes(x=rep(1, 77), y=ProportionCorrect, fill = Mediansplit_midtesting_entiresample))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean proportion of searches correct")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Foil")


p1 +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_point(pch = 21, position = position_jitterdodge(0,0,1.5)) +
  scale_fill_discrete(name = "Age group midtesting (median split)", labels = c("young, n = 35", "old, n = 42"))
```

## Plot age as continuous variable against proportion correct
```{r}
p1<- ggplot(Foil.valid.T1.critreached, aes(x=Midtesting_age_months , y=ProportionCorrect)) + geom_point()+
 labs(x="Age in months",y="Proportion correct")

p1 +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

# Cumulative proportion correct
```{r}
#Trial 1
Foil.trial1<-subset(Foil.valid.T1.critreached, Trial_Nr == "1")

#Trial 2
Foil.trial2<-subset(Foil.valid.T1.critreached, Trial_Nr == "2")

#Trial 3
Foil.trial3<-subset(Foil.valid.T1.critreached, Trial_Nr == "3")

#Trial 4
Foil.trial4<-subset(Foil.valid.T1.critreached, Trial_Nr == "4")

#Trial 5
Foil.trial5<-subset(Foil.valid.T1.critreached, Trial_Nr == "5")

#Trial 6
Foil.trial6<-subset(Foil.valid.T1.critreached, Trial_Nr == "6")

#Trial 7
Foil.trial7<-subset(Foil.valid.T1.critreached, Trial_Nr == "7")

#Trial 8
Foil.trial8<-subset(Foil.valid.T1.critreached, Trial_Nr == "8")


mean(Foil.trial1$CumulativeProportionCorrect)#.59
sd(Foil.trial1$CumulativeProportionCorrect)#.49

mean(Foil.trial2$CumulativeProportionCorrect)#.60
sd(Foil.trial2$CumulativeProportionCorrect)#.37

mean(Foil.trial3$CumulativeProportionCorrect)#.59
sd(Foil.trial3$CumulativeProportionCorrect)#.30

mean(Foil.trial4$CumulativeProportionCorrect)#.59
sd(Foil.trial4$CumulativeProportionCorrect)#.27

mean(Foil.trial5$CumulativeProportionCorrect)#.60
sd(Foil.trial5$CumulativeProportionCorrect)#.24

mean(Foil.trial6$CumulativeProportionCorrect)#.60
sd(Foil.trial6$CumulativeProportionCorrect)#.23

mean(Foil.trial7$CumulativeProportionCorrect)#.59
sd(Foil.trial7$CumulativeProportionCorrect)#.20

mean(Foil.trial8$CumulativeProportionCorrect)#.57
sd(Foil.trial8$CumulativeProportionCorrect)#.20

```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
Graph <-read.csv("CumulPropCorrect.csv",header=TRUE, sep = ";")
names(Graph)[1] <- "Trial_nr"
```

```{r}
library(ggplot2)

ggplot(Graph, aes(x=Trial_nr, y=Mean_proportionCorrect)) + 
    geom_errorbar(aes(ymin=Mean_proportionCorrect-SD_ProportionCorrect, ymax=Mean_proportionCorrect+SD_ProportionCorrect), width=.1) +
    geom_line() +
    geom_point()+
  ylim(0,1.2)
```

We use the arbitrary rule to decide that we want to include anyone who has done 75% of the trials, i.e., 6 trials and up. This means that we can include 1 child. We do that and re-run all the previous lines and find no change.

# Can age and trial number predict children's success?
```{r}
library(lme4)
Foil.valid <-subset(Foil, Dropout =="no" & Warm.up.Crit.reached =="yes, within 2 trials" | Warm.up.Crit.reached =="yes, within 7 trials")

Foil.valid$z.age=as.vector(scale(Foil.valid$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(Foil.valid$z.age)#check whether it has worked
sd(Foil.valid$z.age)

Foil.valid$z.trial=as.vector(scale(Foil.valid$Trial_Nr))#transform trial to mean of 0 and SD of 1
mean(Foil.valid$z.trial)#check whether it has worked
sd(Foil.valid$z.trial)

contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res<-glmer(Trial_correct ~ z.age + z.trial + z.age:z.trial + (1+z.trial|ID), data=Foil.valid, family=binomial, control=contr)

null <- glmer(Trial_correct ~ 1 + (1+z.trial|ID), data=Foil.valid, family=binomial, control=contr)

anova(null, res, test="Chisq")#significant
```
Trial number, age, and the interaction between trial number and age explain the data significantly better than a null model only containing the intercept, X2(3) = 11.415, p = .010.

## Effect of interaction 
```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res.nointer<-glmer(Trial_correct ~ z.age + z.trial + (1+z.trial|ID), data=Foil.valid, family=binomial, control=contr)

anova(res.nointer, res, test="Chisq")
```
The interaction term has no effect, so we remove it from the model.

```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res<-glmer(Trial_correct ~ z.age + z.trial + (1+z.trial|ID), data=Foil.valid, family=binomial, control=contr)

anova(null, res, test="Chisq")

summary(res)
```
Trial number and age explain the data significantly better than a null model only containing the intercept, X2(2) = 11.4, p = .003

## Effect of terms
```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res.noage<-glmer(Trial_correct ~ z.trial + (1+z.trial|ID), data=Foil.valid, family=binomial, control=contr)

anova(res.noage, res, test="Chisq")
```
There is a significant positive effect of age, X2(1) = 6.858, p = .009.

```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res.notrial<-glmer(Trial_correct ~ z.age + (1+z.trial|ID), data=Foil.valid, family=binomial, control=contr)

anova(res.notrial, res, test="Chisq")
```
There is a significant negative effect of trial, X2(1) = 4.526, p = .033.

## Model assumptions
```{r}
source("diagnostic_fcns.r")
ranef.diagn.plot(res)

#collinearity
xres=lm(Trial_correct ~ z.age + z.trial , data=Foil.valid)

library(car)
vif(xres)

source("glmm_stability.r")
m.stab=glmm.model.stab(model.res=res)
m.stab$summary
```

```{r}
source("boot_glmm.r")#requires centering of all predictors apart the ones one is interested in. We are interested in both.

boot.res=boot.glmm.pred(model.res=res, excl.warnings=T,
nboots=1000, para=F, resol=8, use="z.trial")

boot.res$ci.estimates
boot.res$ci.predicted

par(mar=c(3, 3, 0.2, 0.2), mgp=c(1.7, 0.3, 0), las=1, tcl=-0.15)
plot(x=Foil.valid$Trial_Nr, y=Foil.valid$Trial_correct, pch=19, las=2, ylim=c(0, 1),
xlab="Trial number", ylab="Probability of success", cex=0.1*sqrt(Foil.valid$ID))

plot.xvals=seq(from=min(Foil.valid$Trial_Nr), to=max(Foil.valid$Trial_Nr),
length.out=8)

lines(x=plot.xvals, y=boot.res$ci.predicted$fitted,
lty=2)
lines(x=plot.xvals, y=boot.res$ci.predicted$lower.cl,
lty=3)
lines(x=plot.xvals, y=boot.res$ci.predicted$upper.cl,
lty=3)
```

# Effect of Principal components?
```{r}
Foil.valid <-subset(Foil, Dropout =="no" & Warm.up.Crit.reached =="yes, within 2 trials" | Warm.up.Crit.reached =="yes, within 7 trials")
Foil.valid.PC <- subset(Foil.valid, PC1 !="NA")

Foil.valid.PC$z.age=as.vector(scale(Foil.valid.PC$Midtesting_age_months))#transform age to mean of 0 and SD of 1
mean(Foil.valid.PC$z.age)#check whether it has worked
sd(Foil.valid.PC$z.age)

Foil.valid.PC$z.trial=as.vector(scale(Foil.valid.PC$Trial_Nr))#transform trial to mean of 0 and SD of 1
mean(Foil.valid.PC$z.trial)#check whether it has worked
sd(Foil.valid.PC$z.trial)

contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res<-glmer(Trial_correct ~ PC1 + PC2 + z.age + z.trial + (1+z.trial|ID), data=Foil.valid.PC, family=binomial, control=contr)#singular fit

res<-glmer(Trial_correct ~ PC1 + PC2 + z.age + z.trial + (1|ID) + (0+z.trial|ID), data=Foil.valid.PC, family=binomial, control=contr)#singular fit

null <- glmer(Trial_correct ~ 1 + (1|ID) + (0+z.trial|ID), data=Foil.valid.PC, family=binomial, control=contr)

anova(null, res, test="Chisq")#marginally significant
summary(res)
```
```
Together, age, trial number and the two principal components cannot explain the data better than a null model, X2(4) = 9.204, p = .056.