---
title: "Inhibition Boxes"
author: "Eva Reindl"
date: "6 4 2020"
output: word_document
---


```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA
setwd("C:\\")#sets the working directory, this is where your datafile is
GC <-read.csv("Glassceiling.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
names(GC)[1] <- "ID"
GC$NrMistakes_after_FirstTimeReachToOpaquebox<-as.numeric(as.character(GC$NrMistakes_after_FirstTimeReachToOpaquebox))
str(GC)
```
133 children are in the dataset.

# Dropouts
```{r}
GC.dropout<-subset(GC, Dropout == "yes")
```
We have **7 dropouts**:

- 3x sticker was not visible (all female)
- 1 x child stopped after 3 trials (male)
- 1x in trial 9 saw egg in opaque box (female)
- 1 x stopped game after 7 trials (female)
- 1 x stopped game after 2 trials (female)

# Valid data
```{r}
GC.valid<-subset(GC, Dropout == "no")
GC.correct<- aggregate(TotalNrCorrecttrials ~ ID, GC.valid, mean)
```
There are **126 valid cases** in the glass ceiling task.


We decide - also in line with our decisions for the rest of the tasks - that we include all children who have completed 75% of the trials, which is 9 trials or above. We find that none of the children in the dropouts fulfil this criterion, so the final dataset is still 126.

# Description of sample 
## Gender
```{r}
GC.validT1<-subset(GC.valid, Trial.Nr == "1")
table(GC.validT1$Gender)
```
There are **67 females** and **59 males**.

## Age
### Age at the beginning of testing
```{r}
mean(GC.validT1$Age_months)
sd(GC.validT1$Age_months)
min(GC.validT1$Age_months)
max(GC.validT1$Age_months)

table(GC.validT1$Age_group)
```
At the beginning of testing, children included in the glass-ceiling task were on average 48.91 months old (SD = 6.96, range 36-70). There were  57 3-year-olds, 62 4-year-olds, and 7 5-year-olds.

### In the middle of testing
```{r}
mean(GC.validT1$AgeMonths_midtesting)
sd(GC.validT1$AgeMonths_midtesting)
min(GC.validT1$AgeMonths_midtesting)
max(GC.validT1$AgeMonths_midtesting)

hist(GC.validT1$AgeMonths_midtesting,
     main="Age distribution", 
     xlab="Age in months", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(36,75))

table(GC.validT1$AgeGroup_midtesting)
```
In the middle of testing, children included in the glass-ceiling task were on average **49.95 months old (SD = 6.94, range 36-72)**. There were  

- 55 3-year-olds
- 60 4-year-olds
- 10 5-year-olds
- 1 6-year-old

### Age mediansplit (based on entire sample)
```{r}
table(GC.validT1$Mediansplit_midtesting_entiresample)
table(GC.validT1$Mediansplit_midtesting_entiresample, GC.validT1$Gender)
```
There were **64 young** (35 f, 29 m) and **62 old** (32 f, 30 m) children.

## Testing location
```{r}
table(GC.validT1$TestingLocation)
tapply(GC.validT1$AgeMonths_midtesting, GC.validT1$TestingLocation, mean)
tapply(GC.validT1$AgeMonths_midtesting, GC.validT1$TestingLocation, sd)
tapply(GC.validT1$AgeMonths_midtesting, GC.validT1$TestingLocation, min)
tapply(GC.validT1$AgeMonths_midtesting, GC.validT1$TestingLocation, max)
```
There were 58 children from Edinburgh and 69 children from Fife.

- Edinburgh: M = 49.38 months (SD = 5.83, range 36-58)
- Fife: M = 50.44 months (SD = 7.77, range 38-72)

# First box chosen
```{r}
table(GC.validT1$FirstBoxChosen)
table(GC.validT1$FirstBoxChosen, GC.validT1$AgeGroup_midtesting)
table(GC.validT1$FirstBoxChosen, GC.validT1$Mediansplit_midtesting_entiresample)
```
**111 out of 126 children (88%)** chose the transparent box first, while 15 (12%) picked the opaque box first.

- 3-year-olds (n= 55): 51 (93%) picked transparent, 4 opaque
- 4-year-olds (n = 60): 49 (82%)picked transparent, 11 opaque
- 5-year-olds (n = 10): 10 (100%) picked transparent, 0 opaque
- 6-year-olds (n = 1): 1 (100%) picked transparent

- Young children (n = 64): 57 (89%) picked transparent, 7 opaque
- Old children: (n = 62): 54 (87%) picked transparent, 8 opaque


# Run length
```{r}
table(GC.validT1$RunLength_ifFirstMoveWasToStickerbox)
hist(GC.validT1$RunLength_ifFirstMoveWasToStickerbox)
mean(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, na.rm = T)
sd(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, na.rm = T)
min(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, na.rm = T)
max(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, na.rm = T)

tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$AgeGroup_midtesting, mean, na.rm = T)
tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$AgeGroup_midtesting, sd, na.rm = T)
tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$AgeGroup_midtesting, min, na.rm = T)
tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$AgeGroup_midtesting, max, na.rm = T)

tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$Mediansplit_midtesting_entiresample, mean, na.rm = T)
tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$Mediansplit_midtesting_entiresample, sd, na.rm = T)
tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$Mediansplit_midtesting_entiresample, min, na.rm = T)
tapply(GC.validT1$RunLength_ifFirstMoveWasToStickerbox, GC.validT1$Mediansplit_midtesting_entiresample, max, na.rm = T)
```
Out of the 111 children who chose a transparent box first, 68 children **(61%) then tried the opaque box in trial 2**. The remaining children had **run lengths of mostly 2 or 3 trials, but there were also 7 children who never tried the opaque box**. Mean run length was **2.48 (SD = 2.90, range 1-12)**. 

- 3y: 2.70 (SD = 2.93, range 1-12)
- 4y: 2.28 (SD = 2.83, range 1-12)
- 5y: 2.40 (SD = 3.44, range 1-12)
- 6y: 1

- Young: 2.60 (SD = 2.81, range 1-12)
- Old: 2.35 (SD = 3.02, range 1-12)

# Number of correct trials
```{r}
mean(GC.validT1$TotalNrCorrecttrials)
sd(GC.validT1$TotalNrCorrecttrials)
min(GC.validT1$TotalNrCorrecttrials)
max(GC.validT1$TotalNrCorrecttrials)
hist(GC.validT1$TotalNrCorrecttrials)
shapiro.test(GC.validT1$TotalNrCorrecttrials)

tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$AgeGroup_midtesting, mean)
tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$AgeGroup_midtesting, sd)
tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$AgeGroup_midtesting, min)
tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$AgeGroup_midtesting, max)

tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$Mediansplit_midtesting_entiresample, mean)
tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$Mediansplit_midtesting_entiresample, sd)
tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$Mediansplit_midtesting_entiresample, min)
tapply(GC.validT1$TotalNrCorrecttrials, GC.validT1$Mediansplit_midtesting_entiresample, max)
```
The average number of correct trials was **8.89 (SD = 2.86, range 0-12)**. The variable is not normally distributed, W = 0.741, p < .001.


- 3y: 8.54 (SD = 2.95, range 0-11)
- 4y: 9.15 (SD = 2.74, range 0-12)
- 5y: 9.00 (SD = 3.26, range 0-11)
- 6y: 11

- Young: 8.73 (SD = 2.82, range 0-11)
- Old: 9.05 (SD = 2.92, range 0-12)

# Number of errors
```{r}
mean(GC.validT1$TotalNrErrors)
sd(GC.validT1$TotalNrErrors)
min(GC.validT1$TotalNrErrors)
max(GC.validT1$TotalNrErrors)
hist(GC.validT1$TotalNrErrors)
shapiro.test(GC.validT1$TotalNrErrors)

tapply(GC.validT1$TotalNrErrors, GC.validT1$AgeGroup_midtesting, mean)
tapply(GC.validT1$TotalNrErrors, GC.validT1$AgeGroup_midtesting, sd)
tapply(GC.validT1$TotalNrErrors, GC.validT1$AgeGroup_midtesting, min)
tapply(GC.validT1$TotalNrErrors, GC.validT1$AgeGroup_midtesting, max)

tapply(GC.validT1$TotalNrErrors, GC.validT1$Mediansplit_midtesting_entiresample, mean)
tapply(GC.validT1$TotalNrErrors, GC.validT1$Mediansplit_midtesting_entiresample, sd)
tapply(GC.validT1$TotalNrErrors, GC.validT1$Mediansplit_midtesting_entiresample, min)
tapply(GC.validT1$TotalNrErrors, GC.validT1$Mediansplit_midtesting_entiresample, max)
```
The average number of errors was **3.11 (SD = 2.86, range 0-12)**. The variable is not normally distributed, W = 0.741, p < .001.

- 3y: 3.45 (SD = 2.95, range 1-12)
- 4y: 2.85 (SD = 2.74, range 0-12)
- 5y: 3 (SD = 3.26, range 1-12)
- 6y: 1

- Young: 3.26 (SD = 2.82, range 1-12)
- Old: 2.95 (SD = 2.92, range 0-12)

# Number of mistakes after first reach to opaque box
```{r}
table(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox)
mean(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, na.rm = T)
sd(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, na.rm = T)
min(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, na.rm = T)
max(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, na.rm = T)
hist(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox)

table(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$AgeGroup_midtesting)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$AgeGroup_midtesting, mean, na.rm = T)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$AgeGroup_midtesting, sd, na.rm = T)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$AgeGroup_midtesting, min, na.rm = T)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$AgeGroup_midtesting, max, na.rm = T)

table(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$Mediansplit_midtesting_entiresample)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$Mediansplit_midtesting_entiresample, mean, na.rm = T)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$Mediansplit_midtesting_entiresample, sd, na.rm = T)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$Mediansplit_midtesting_entiresample, min, na.rm = T)
tapply(GC.validT1$NrMistakes_after_FirstTimeReachToOpaquebox, GC.validT1$Mediansplit_midtesting_entiresample, max, na.rm = T)

```
119 children (94%) reached to the opaque (correct) box at least once. For those children, **the average number of mistakes after reaching to the correct box first was 0.97 (SD = 1.52, range 0-8)**. The variable was highly skewed.

- 3y (n = 52): 1.00 (SD = 1.69, range 0-8)
- 4y ( n = 57): 1.00 (SD = 1.49, range 0-7)
- 5y (n = 9): 0.67 (SD = 0.5, range 0-1)
- 6y (n = 1): 0

- Young (n = 61): 0.98 (SD = 1.59, range 0-8)
- Old (n = 58): 0.95 (SD = 1.47, range 0-7)

# DV: Proportion of correct trials
```{r}
mean(GC.validT1$ProportionCorrect)
sd(GC.validT1$ProportionCorrect)
min(GC.validT1$ProportionCorrect)
max(GC.validT1$ProportionCorrect)
shapiro.test(GC.validT1$ProportionCorrect)

hist(GC.validT1$ProportionCorrect,
     main="Proportion of correct trials across sample", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

wilcox.test(GC.validT1$ProportionCorrect, mu = 0.5, alternative = "two.sided")


tapply(GC.validT1$ProportionCorrect, GC.validT1$AgeGroup_midtesting, mean)
tapply(GC.validT1$ProportionCorrect, GC.validT1$AgeGroup_midtesting, sd)
tapply(GC.validT1$ProportionCorrect, GC.validT1$AgeGroup_midtesting, min)
tapply(GC.validT1$ProportionCorrect, GC.validT1$AgeGroup_midtesting, max)

three <- subset(GC.validT1, AgeGroup_midtesting == "3")
four <- subset(GC.validT1, AgeGroup_midtesting == "4")
five <- subset(GC.validT1, AgeGroup_midtesting == "5")

shapiro.test(three$ProportionCorrect)
shapiro.test(four$ProportionCorrect)
shapiro.test(five$ProportionCorrect)

hist(three$ProportionCorrect,
     main="3-year-olds", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(four$ProportionCorrect,
     main="4-year-olds", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(five$ProportionCorrect,
     main="5-year-olds", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

wilcox.test(three$ProportionCorrect, mu = 0.5, alternative = "two.sided")
wilcox.test(four$ProportionCorrect, mu = 0.5, alternative = "two.sided")
wilcox.test(five$ProportionCorrect, mu = 0.5, alternative = "two.sided")

Onlythreeandfour <- subset(GC.validT1, AgeGroup_midtesting == "3" | AgeGroup_midtesting == "4")
wilcox.test(Onlythreeandfour$ProportionCorrect ~ Onlythreeandfour$AgeGroup_midtesting, alternative = "less")


tapply(GC.validT1$ProportionCorrect, GC.validT1$Mediansplit_midtesting_entiresample, mean)
tapply(GC.validT1$ProportionCorrect, GC.validT1$Mediansplit_midtesting_entiresample, sd)
tapply(GC.validT1$ProportionCorrect, GC.validT1$Mediansplit_midtesting_entiresample, min)
tapply(GC.validT1$ProportionCorrect, GC.validT1$Mediansplit_midtesting_entiresample, max)

young <- subset(GC.validT1, Mediansplit_midtesting_entiresample == "young")
old <- subset(GC.validT1, Mediansplit_midtesting_entiresample == "old")

shapiro.test(young$ProportionCorrect)
shapiro.test(old$ProportionCorrect)

hist(young$ProportionCorrect,
     main="Young children", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(old$ProportionCorrect,
     main="Old children", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

wilcox.test(young$ProportionCorrect, mu = 0.5, alternative = "two.sided")
wilcox.test(old$ProportionCorrect, mu = 0.5, alternative = "two.sided")

wilcox.test(GC.validT1$ProportionCorrect ~ GC.validT1$Mediansplit_midtesting_entiresample, alternative = "greater")

tapply(GC.validT1$ProportionCorrect, GC.validT1$TestingLocation, mean)
tapply(GC.validT1$ProportionCorrect, GC.validT1$TestingLocation, sd)
tapply(GC.validT1$ProportionCorrect, GC.validT1$TestingLocation, min)
tapply(GC.validT1$ProportionCorrect, GC.validT1$TestingLocation, max)

Edi <- subset(GC.validT1, TestingLocation == "Edinburgh")
Fife <- subset(GC.validT1, TestingLocation == "Fife")

shapiro.test(Edi$ProportionCorrect)
shapiro.test(Fife$ProportionCorrect)

hist(Edi$ProportionCorrect,
     main="Children from Edinburgh", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

hist(Fife$ProportionCorrect,
     main="Children from Fife", 
     xlab="Proportion of correct trials", 
     ylab="Number of children",
     border="black", 
     col="grey",
     xlim=c(0,1))

wilcox.test(Edi$ProportionCorrect, mu = 0.5, alternative = "two.sided")
wilcox.test(Fife$ProportionCorrect, mu = 0.5, alternative = "two.sided")

wilcox.test(GC.validT1$ProportionCorrect ~ GC.validT1$TestingLocation, alternative = "two.sided")
```
The mean proportion of correct trials was **0.74 (SD = 0.24, range 0-1)**. The variable is **not normally distributed**, W = 0.741, p < .001. Children's **performance is significantly higher than what would be expected by chance (0.5)**, two-sided Wilcoxon test, V = 6121, p < .001.

- **3y: 0.71** (SD = 0.24, range 0-0.92), not normally distributed, W = 0.779, p < .001. Significantly above chance, V = 1087, p < .001
- **4y: 0.76** (SD = 0.23, range 0-1), not normally distributed, W = 0.727, p < .001. Significantly above chance, V = 1479.5, p < .001
- **5y: 0.75** (SD = 0.27, range 0-0.92), not normally distributed, W = 0.555, p < .001. At chance level, V = 45, p = .076
- **6y: 0.92**

**4-year-olds do not perform better than 3-year-olds**, one-sided Wilcoxon test, W = 1416, p = .090.


- Young: 0.73 (SD = 0.23, range 0-0.92), not normally distributed, W = 0.760, p < .001. Significantly above chance, V = 1496.5, p < .001
- Old: 0.75 (SD = 0.24, range 0-1), not normally distributed, W = 0.710, p < .001. Significantly above chance, V = 1591, p < .001

**Old children do not perform  better than young children**, one-sided Wilcoxon test, W = 2165.5, p = .182.

- Edinburgh: 0.79 (SD = 0.14, range 0.5-1), not normally distributed, W = 0.841, p < .001. Significantly above chance, V = 1326, p < .001
- Fife: 0.70 (SD = 0.29, range 0-1), not normally distributed, W = 0.728, p < .001. Significantly above chance, V = 1771.5, p < .001

Children from Edinburgh do not perform differently than children from Fife, two-sided Wilcoxon test, W = 2234.5, p = .188.

```{r}
#Plot, across ages
library(ggplot2)
p<-  ggplot(
  data=GC.validT1, aes(x=rep(1, 126), y=ProportionCorrect)) +
  geom_boxplot(outlier.colour = "black")+
  ylim(0, 1)+
  xlim(0,2)+
  labs(x="",y="Mean proportion of correct trials")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Boxes")

p + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) + geom_count()+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")



#Plot, by age groups
p1<-ggplot(data=GC.validT1, aes(x=AgeGroup_midtesting,y=ProportionCorrect)) +
  geom_boxplot(aes(group=AgeGroup_midtesting, fill = as.factor(GC.validT1$AgeGroup_midtesting)), outlier.colour = "black") + 
      ylim(0,1)+
  xlim(2.5,6.5)+
  geom_point(alpha=0.3) +
  geom_hline(yintercept=.5, colour = "red") +
  labs(x="",y="Mean proportion of correct choices")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Boxes")

p1  +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_count(colour = "black", position = position_jitterdodge(0,0,1), alpha = 0.5)+
  scale_fill_discrete(name = "Age group midtesting", labels = c("3 years, n = 55", "4 years, n = 60", "5 years, n = 10", "6 years, n = 1"))+
  theme(legend.title = element_blank())


#Plot, by age mediansplit
library(forcats)

GC.validT1$Mediansplit_midtesting_entiresample<-fct_relevel(GC.validT1$Mediansplit_midtesting_entiresample, "young")
#changes order of boxplots (young before old)

p1<-  ggplot(
  data=GC.validT1, aes(x=rep(1, 126), y=ProportionCorrect, fill = Mediansplit_midtesting_entiresample))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean proportion of correct choices")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Boxes")

p1 +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_point(pch = 21, position = position_jitterdodge(0,0,1.5)) +
  scale_fill_discrete(name = "Age group midtesting (median split)", labels = c("young (36-49 months), n = 64", "old (50-72 months), n = 62"))



#Plot, by testing location
p1<-  ggplot(
  data=GC.validT1, aes(x=rep(1, 126), y=ProportionCorrect, fill = TestingLocation))+
  geom_boxplot(outlier.colour = "black", position=position_dodge(1.5))+
  ylim(0,1)+
  xlim(0,2)+
  labs(x="",y="Mean proportion of correct trials")+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Inhibition Boxes")

p1 +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ theme(axis.text.x = element_blank()) + theme(axis.ticks.x = element_blank()) +
  geom_point(pch = 21, position = position_jitterdodge(0,0,1.5)) +
  scale_fill_discrete(name = "Testing location", labels = c("Edinburgh, n = 58", "Fife, n = 68"))
```

## Plot age as continuous variable against proportion correct
```{r}
p1<- ggplot(GC.validT1, aes(x=AgeMonths_midtesting, y=ProportionCorrect)) + geom_point()

p1 +  geom_hline(yintercept=0.5, linetype="dashed", color = "red") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```




# Cumulative proportion correct
```{r}
#Trial 1
GC.trial1<-subset(GC, Dropout == "no" & Trial.Nr == "1")

#Trial 2
GC.trial2<-subset(GC, Dropout == "no" & Trial.Nr == "2")

#Trial 3
GC.trial3<-subset(GC, Dropout == "no" & Trial.Nr == "3")

#Trial 4
GC.trial4<-subset(GC, Dropout == "no" & Trial.Nr == "4")

#Trial 5
GC.trial5<-subset(GC, Dropout == "no" & Trial.Nr == "5")

#Trial 6
GC.trial6<-subset(GC, Dropout == "no" & Trial.Nr == "6")

#Trial 7
GC.trial7<-subset(GC, Dropout == "no" & Trial.Nr == "7")

#Trial 8
GC.trial8<-subset(GC, Dropout == "no" & Trial.Nr == "8")

#Trial 9
GC.trial9<-subset(GC, Dropout == "no" & Trial.Nr == "9")

#Trial 10
GC.trial10<-subset(GC, Dropout == "no" & Trial.Nr == "10")

#Trial 11
GC.trial11<-subset(GC, Dropout == "no" & Trial.Nr == "11")

#Trial 12
GC.trial12<-subset(GC, Dropout == "no" & Trial.Nr == "12")

mean(GC.trial1$Cumulative_ProportionCorrect)#11.90
sd(GC.trial1$Cumulative_ProportionCorrect)#32.51

mean(GC.trial2$Cumulative_ProportionCorrect)#36.11
sd(GC.trial2$Cumulative_ProportionCorrect)#28.73

mean(GC.trial3$Cumulative_ProportionCorrect)#43.65
sd(GC.trial3$Cumulative_ProportionCorrect)#29.95

mean(GC.trial4$Cumulative_ProportionCorrect)#51.59
sd(GC.trial4$Cumulative_ProportionCorrect)#28.06

mean(GC.trial5$Cumulative_ProportionCorrect)#58.09
sd(GC.trial5$Cumulative_ProportionCorrect)#27.06

mean(GC.trial6$Cumulative_ProportionCorrect)#62.17
sd(GC.trial6$Cumulative_ProportionCorrect)#26.37

mean(GC.trial7$Cumulative_ProportionCorrect)#64.96
sd(GC.trial7$Cumulative_ProportionCorrect)#25.91

mean(GC.trial8$Cumulative_ProportionCorrect)#67.26
sd(GC.trial8$Cumulative_ProportionCorrect)#25.39

mean(GC.trial9$Cumulative_ProportionCorrect)#69.40
sd(GC.trial9$Cumulative_ProportionCorrect)#24.53

mean(GC.trial10$Cumulative_ProportionCorrect)#70.95
sd(GC.trial10$Cumulative_ProportionCorrect)#24.54


mean(GC.trial11$Cumulative_ProportionCorrect)#72.80
sd(GC.trial11$Cumulative_ProportionCorrect)#24.13

mean(GC.trial12$Cumulative_ProportionCorrect)#74.14
sd(GC.trial12$Cumulative_ProportionCorrect)#23.89

#medians
q1 <-quantile(GC.trial1$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#0
q2 <-quantile(GC.trial2$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.5
q3 <-quantile(GC.trial3$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.66.67
q4 <-quantile(GC.trial4$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#0.5
q5 <-quantile(GC.trial5$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#0.6
q6 <-quantile(GC.trial6$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.667
q7 <-quantile(GC.trial7$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#71
q8 <-quantile(GC.trial8$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#75
q9 <-quantile(GC.trial9$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.77
q10 <-quantile(GC.trial10$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.80
q11 <-quantile(GC.trial11$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.82
q12 <-quantile(GC.trial12$Cumulative_ProportionCorrect, probs = c(.25,.5,.75))#.83
Q <- data.frame(c(q1, q2, q3, q4, q5, q6, q7, q8, q9, q10, q11, q12))
Q

#We put these data into a new excel file (see below).

#LOAD DATA
CumGC <-read.csv("CumPropCorrectGlassceiling.csv",header=TRUE, sep = ";")
names(CumGC)[1] <- "Trial_nr"

ggplot(CumGC, aes(x=Trial_nr, y=Mean_proportionCorrect)) + 
    geom_errorbar(aes(ymin=Mean_proportionCorrect-SD_ProportionCorrect, ymax=Mean_proportionCorrect+SD_ProportionCorrect), width=.1) +
    geom_line() +
    geom_point()+
    geom_hline(yintercept=74.14)
  ylim(-30, 100)
```



# Can children's success be predicted by trial number, age and testing location?
```{r}
library(lme4)

#we z-transform age and trial number, as we are including them into an interaction
GC.valid$z.age.midtesting=as.vector(scale(GC.valid$AgeMonths_midtesting))#transform age to mean of 0 and SD of 1
mean(GC.valid$z.age.midtesting)#check whether it has worked
sd(GC.valid$z.age.midtesting)

GC.valid$z.Trial_nr=as.vector(scale(GC.valid$Trial.Nr))#transform trial number to mean of 0 and SD of 1
mean(GC.valid$z.Trial_nr)#check whether it has worked
sd(GC.valid$z.Trial_nr)

#Full model
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res<-glmer(Trial_Correct ~ z.age.midtesting + z.Trial_nr + TestingLocation + z.age.midtesting:z.Trial_nr + (1+z.Trial_nr|ID), data=GC.valid, family = binomial, control=contr)
```

Comparison against null model
```{r}
null<-glmer(Trial_Correct ~ 1 + (1+z.Trial_nr|ID), data=GC.valid, family = binomial, control=contr)

anova(null, res, test="Chisq")
```
Together, age, trial number, the interaction between trial number and age, and testing location can explain the data significantly better than a null model only containing the intercept, X2(4) = 116.11, p < .001.

**Effect of the interaction term**
```{r}
res.nointer<-glmer(Trial_Correct ~ z.age.midtesting + z.Trial_nr + TestingLocation + (1+z.Trial_nr|ID), data=GC.valid, family = binomial, control=contr)
anova(res.nointer, res, test="Chisq")
```
There is no effect of the interaction term, X2(1) = 0.002, p = .960, so we remove it from the model.

New full model
```{r}
res<-glmer(Trial_Correct ~ z.age.midtesting + z.Trial_nr + TestingLocation + (1+z.Trial_nr|ID), data=GC.valid, family = binomial, control=contr)
anova(null, res, test="Chisq")
```
The full model can explain the data significantly better than a null model only containing the intercept, X2(3) = 116.11, p < .001.

**Estimate of testing location**
```{r}
res.notest<-glmer(Trial_Correct ~ z.age.midtesting + z.Trial_nr + (1+z.Trial_nr|ID), data=GC.valid, family = binomial, control=contr)
anova(res.notest, res, test="Chisq")
```
Testing location cannot improve model fit, X2(1) = 2.617, p = .106, so we remove it from the model.


New full model

We include the non-transformed version of trial number
```{r}
res<-glmer(Trial_Correct ~ z.age.midtesting + Trial.Nr + (1+Trial.Nr|ID), data=GC.valid, family = binomial, control=contr)
null<-glmer(Trial_Correct ~ 1 + (1+Trial.Nr|ID), data=GC.valid, family = binomial, control=contr)
anova(null, res, test="Chisq")
summary(res)
```
Trial number and age can explain the data significantly better than the null model, X2(2) = 113.49, p < .001.

**Effect of trial number**
```{r}
res.notrial<-glmer(Trial_Correct ~ z.age.midtesting + (1+Trial.Nr|ID), data=GC.valid, family = binomial, control=contr)
anova(res.notrial, res, test="Chisq")
```
Trial number had a significant effect on children's success, X2(1) = 108.7, p < .001. 

**Effect of age**
```{r}
res.noage<-glmer(Trial_Correct ~ Trial.Nr + (1+Trial.Nr|ID), data=GC.valid, family = binomial, control=contr)
anova(res.noage, res, test="Chisq")
```
Age had a significant effect on children's success, X2(1) = 4.506, p = .034.

Confidence intervals
```{r}
source("boot_glmm.r")#requires centering of all predictors apart the ones one is interested in. We are interested in both.
res<-glmer(Trial_Correct ~ z.age.midtesting + z.Trial_nr + (1+z.Trial_nr|ID), data=GC.valid, family = binomial, control=contr)

boot.res=boot.glmm.pred(model.res=res, excl.warnings=T,
nboots=1000, para=T, resol=12, use="z.Trial_nr")
```

Plot the effect of trial number on success
```{r}
par(mar=c(3, 3, 0.2, 0.2), mgp=c(1.7, 0.3, 0), las=1, tcl=-0.15)
plot(x=GC.valid$Trial.Nr, y=GC.valid$Trial_Correct, pch=19, las=2, ylim=c(0, 1),
xlab="Trial number", ylab="Probability of success")

plot.xvals=seq(from=min(GC.valid$Trial.Nr), to=max(GC.valid$Trial.Nr),
length.out=12)

lines(x=plot.xvals, y=boot.res$ci.predicted$fitted,
lty=2)
lines(x=plot.xvals, y=boot.res$ci.predicted$lower.cl,
lty=3)
lines(x=plot.xvals, y=boot.res$ci.predicted$upper.cl,
lty=3)
```


## Model assumptions
```{r}
source("diagnostic_fcns.r")
ranef.diagn.plot(res)

#collinearity
xres=lm(Trial_Correct ~ z.age.midtesting + Trial.Nr, data=GC.valid)

library(car)
vif(xres)

source("glmm_stability.r")
m.stab=glmm.model.stab(model.res=res, contr=contr)
m.stab$summary
```



# Considering BPVS score: Can children's success be predicted by trial number, age and testing location?
```{r}
GC.valid.BPVS <- subset(GC.valid, BPVS_Score !="NA") 

#we z-transform age and trial number, as we are including them into an interaction
GC.valid.BPVS$z.age.midtesting=as.vector(scale(GC.valid.BPVS$AgeMonths_midtesting))#transform age to mean of 0 and SD of 1
mean(GC.valid.BPVS$z.age.midtesting)#check whether it has worked
sd(GC.valid.BPVS$z.age.midtesting)

GC.valid.BPVS$z.Trial_nr=as.vector(scale(GC.valid.BPVS$Trial.Nr))#transform trial number to mean of 0 and SD of 1
mean(GC.valid.BPVS$z.Trial_nr)#check whether it has worked
sd(GC.valid.BPVS$z.Trial_nr)

GC.valid.BPVS$z.BPVS_Score=as.vector(scale(GC.valid.BPVS$BPVS_Score))
mean(GC.valid.BPVS$z.BPVS_Score)#check whether it has worked
sd(GC.valid.BPVS$z.BPVS_Score)

#Full model
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
res<-glmer(Trial_Correct ~ z.BPVS_Score + z.age.midtesting + z.Trial_nr + TestingLocation + z.age.midtesting:z.Trial_nr + (1+z.Trial_nr|ID), data=GC.valid.BPVS, family = binomial, control=contr)
```

Comparison against null model
```{r}
null<-glmer(Trial_Correct ~ 1 + (1+z.Trial_nr|ID), data=GC.valid.BPVS, family = binomial, control=contr)

anova(null, res, test="Chisq")
```
Together, age, BOVS score, trial number, the interaction between trial number and age, and testing location can explain the data significantly better than a null model only containing the intercept, X2(5) = 110.90, p < .001.

**Effect of the interaction term**
```{r}
res.nointer<-glmer(Trial_Correct ~ z.BPVS_Score + z.age.midtesting + z.Trial_nr + TestingLocation + (1+z.Trial_nr|ID), data=GC.valid.BPVS, family = binomial, control=contr)
anova(res.nointer, res, test="Chisq")
```
There is no effect of the interaction term, X2(1) = 0.144, p = .704, so we remove it from the model.

New full model
```{r}
res<-glmer(Trial_Correct ~ z.BPVS_Score + z.age.midtesting + z.Trial_nr + TestingLocation + (1+z.Trial_nr|ID), data=GC.valid.BPVS, family = binomial, control=contr)
anova(null, res, test="Chisq")
```
The full model can explain the data significantly better than a null model only containing the intercept, X2(4) = 110.75, p < .001.

**Estimate of testing location**
```{r}
res.notest<-glmer(Trial_Correct ~ z.BPVS_Score + z.age.midtesting + z.Trial_nr + (1+z.Trial_nr|ID), data=GC.valid.BPVS, family = binomial, control=contr)
anova(res.notest, res, test="Chisq")
```
Testing location cannot improve model fit, X2(1) = 1.600, p = .206.

**Estimate of BPVS score**
```{r}
res.nobpvs<-glmer(Trial_Correct ~ TestingLocation + z.age.midtesting + z.Trial_nr + (1+z.Trial_nr|ID), data=GC.valid.BPVS, family = binomial, control=contr)
anova(res.nobpvs, res, test="Chisq")
```
BPVS score cannot improve model fit, X2(1) = 0.384, p = .535.

